### 2019-12-06 Presentation/Presentation_trial.Rmd
Rename Presentation_trial.Rmd to Presentation/Presentation_trial.Rmd

---
title: "Pre- and Post-Debate Democratic Primary Data: Twitter, Google Trends, and Polls"
subtitle: "SURV 727"
author: "Zoe Padgett and Fatou Thiam"
date: "12/6/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

### 2019-12-06 Paper/paper-draft-Padgett-Thiam.Rmd
move files

---
title: "Fundamentals of Computing and Data Display"
subtitle: "Term paper template"
author: "Author"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: yes
    df_print: kable
references:
- id: Wickham2014
  title: Tidy Data
  author:
  - family: Wickham
    given: Hadley
  container-title: Journal of Statistical Software
  volume: 59
  issue: 10
  page: 1-23
  type: article-journal
  issued:
    year: 2014
- id: Baumer2017
  title: Modern Data Science with R
  author:
  - family: Baumer
    given: Benjamin S.
  - family: Kaplan
    given: Daniel T.
  - family: Horton
    given: Nicholas J.
  type: book
  publisher: Chapman \& Hall/CRC Press.
  issued:
    year: 2017
---

TO DO:
- write intro, results, and discussion sections
- save the following datasets to github and write code in designated chunks to bring them in:
    props_tab1
    props_tab2
    gc_locations
    interest_over_time_all
    pre_sent_pos
    post_sent_pos
- create presentation

```{r, include = FALSE}
library(knitr)
library(tidyverse)
library(gtrendsR)
library(dplyr)
library(ggplot2)
library(ggmap)
library(readxl)
library(shiny)
library(rtweet)
library(tidytext)
library(stringr)
library(lubridate)
library(quanteda)
library(SentimentAnalysis)
library(GGally)
```

## Introduction

This section outlines the research idea. We can also cite related work here [@Wickham2014; @Baumer2017].

Note that compiled term paper (the PDF) is supposed to be more text-centered than the RMarkdown documents we used in class, i.e. the text sections are more detailed and big or redundant code chunks can be hidden.

## Data

This section describes the data sources and the data gathering process.

### Twitter

Below is our token to access the Twitter API and start collecting tweets.

```{r, eval=FALSE}
create_token(
  app = "fcdd-course",
  consumer_key = "7y8Xu96DRkBoLsdP8XbQJXTn9",
  consumer_secret = "MCM7gcAfTJKwHks2yIRZaDZcODRQCJBusiYoZtobj4XvO7bvpV",
  access_token = "967157671353864192-DvdUZcJN1ocpqx74YN2GwyejeIMR1Da",
  access_secret = "KkCoMdH1vuivbWgH6IdDaDuiScNcxr389caRbhG2L2kXW"
)
```

#### Quering Tweets

Using the search_tweets function in the rtweets package, we will be quering tweets with the keywords specified below. We limited our tweets pool to November 20th and November 21st. The reasonning behind this is to get a feel post and pre debate.

```{r, eval=FALSE}

dem <- search_tweets("#democrats OR #candidates OR #election2020 OR #BIDEN OR #sanders OR #warren OR #harris 
                     OR #buttigieg OR #steyer OR #yang OR #booker OR #klobuchar OR #gabbard   
                     OR @KamalaHarris OR @JoeBiden OR @BernieSanders OR @ewarren OR @PeteButtigieg 
                     OR @TomSteyer OR @AndrewYang OR @BookerCory OR @amyklobuchar OR @TulsiGabbard ",  since='2019-11-20', until='2019-11-21', n= 500000,  retryonratelimit = TRUE, verbose = TRUE)
```

#### Data Cleaning

Even after we specify the keywords, we know that we would still get irrelevants tweets mainly with the Ukraine issue at the time of pulling. We removed all tweets that had the word "Ukraine" in it.

```{r, eval=FALSE}
myvars <- c("text", "location", "created_at")
df1 <- dem[myvars]
df2 <- dem2[myvars]
```

```{r, eval=FALSE}
df1 <- df1 %>%
      mutate( ukraine = (str_detect(df1$text, regex("Ukraine", ignore_case = TRUE)))) %>%
      filter(ukraine=="FALSE") %>%
      select(-ukraine)

df2 <- df2 %>%
      mutate( ukraine = (str_detect(df2$text, regex("Ukraine", ignore_case = TRUE)))) %>%
      filter(ukraine=="FALSE") %>%
      select(-ukraine)
```

```{r, eval=FALSE}
tweets <- rbind(df1, df2)

```

Next, we seperate the tweets by candidates in order to do the analysis at the candidate level. It's important to note that one tweets can be addressed to multiple candidates. In that case, the tweet will be found in the each of those candidate dataset.

```{r, eval=FALSE}
tweets$BS <-(str_detect(tweets$text, regex("#Sanders|@BernieSanders", ignore_case = TRUE)))
tweets$KH <-(str_detect(tweets$text, regex("#harris |@KamalaHarris",  ignore_case = TRUE)))
tweets$JB <-(str_detect(tweets$text, regex("#biden |@JoeBiden", ignore_case = TRUE)))
tweets$EW <-(str_detect(tweets$text, regex("#warren |@ewarren", ignore_case = TRUE)))
tweets$PB <-(str_detect(tweets$text, regex("#buttigieg|@PeteButtigieg", ignore_case = TRUE)))
tweets$TS <-(str_detect(tweets$text, regex("#steyer | @TomSteyer", ignore_case = TRUE)))
tweets$AY <-(str_detect(tweets$text, regex("#yang| @AndrewYang", ignore_case = TRUE)))
tweets$BC <-(str_detect(tweets$text, regex("#booker | @BookerCory", ignore_case = TRUE)))
tweets$AK <-(str_detect(tweets$text, regex("#klobuchar | @amyklobuchar", ignore_case = TRUE)))
tweets$TG <-(str_detect(tweets$text, regex("#gabbard |@TulsiGabbard", ignore_case = TRUE)))

```

```{r, eval=FALSE}
df1$BS <-(str_detect(df1$text, regex("#Sanders|@BernieSanders", ignore_case = TRUE)))
df1$KH <-(str_detect(df1$text, regex("#harris |@KamalaHarris",  ignore_case = TRUE)))
df1$JB <-(str_detect(df1$text, regex("#biden |@JoeBiden", ignore_case = TRUE)))
df1$EW <-(str_detect(df1$text, regex("#warren |@ewarren", ignore_case = TRUE)))
df1$PB <-(str_detect(df1$text, regex("#buttigieg|@PeteButtigieg", ignore_case = TRUE)))
df1$TS <-(str_detect(df1$text, regex("#steyer | @TomSteyer", ignore_case = TRUE)))
df1$AY <-(str_detect(df1$text, regex("#yang| @AndrewYang", ignore_case = TRUE)))
df1$BC <-(str_detect(df1$text, regex("#booker | @BookerCory", ignore_case = TRUE)))
df1$AK <-(str_detect(df1$text, regex("#klobuchar | @amyklobuchar", ignore_case = TRUE)))
df1$TG <-(str_detect(df1$text, regex("#gabbard |@TulsiGabbard", ignore_case = TRUE)))

```

```{r, eval=FALSE}
df2$BS <-(str_detect(df2$text, regex("#Sanders|@BernieSanders", ignore_case = TRUE)))
df2$KH <-(str_detect(df2$text, regex("#harris |@KamalaHarris",  ignore_case = TRUE)))
df2$JB <-(str_detect(df2$text, regex("#biden |@JoeBiden", ignore_case = TRUE)))
df2$EW <-(str_detect(df2$text, regex("#warren |@ewarren", ignore_case = TRUE)))
df2$PB <-(str_detect(df2$text, regex("#buttigieg|@PeteButtigieg", ignore_case = TRUE)))
df2$TS <-(str_detect(df2$text, regex("#steyer | @TomSteyer", ignore_case = TRUE)))
df2$AY <-(str_detect(df2$text, regex("#yang| @AndrewYang", ignore_case = TRUE)))
df2$BC <-(str_detect(df2$text, regex("#booker | @BookerCory", ignore_case = TRUE)))
df2$AK <-(str_detect(df2$text, regex("#klobuchar | @amyklobuchar", ignore_case = TRUE)))
df2$TG <-(str_detect(df2$text, regex("#gabbard |@TulsiGabbard", ignore_case = TRUE)))

```

Here we reformat the created_at column as a date & time variable in order to seperate the tweets in two groups : post and pre debate.
```{r, eval=FALSE}
tweets <- tweets %>%
  mutate( date= as.POSIXct(created_at, tryFormats = c("%Y-%m-%d %H:%M:%OS")))

df1 <- df1 %>%
    mutate( date= as.POSIXct(created_at, tryFormats = c("%Y-%m-%d %H:%M:%OS")))

df2 <- df2 %>%
    mutate( date= as.POSIXct(created_at, tryFormats = c("%Y-%m-%d %H:%M:%OS")))

```

All the tweets received before 9 p.m. on November 20th are accounted for in the pre-debate dataset and all tweets from 11 p.m. on November 20th to the next day are in the post-debate dataset. Note that tweets during the debate( 9 - 11 p.m are ignored)
```{r, eval=FALSE}
pre_debate <- tweets %>%
              filter(date(date) == "2019-11-20" & hour(date) < 21 )

post_debate <- tweets %>%
              filter(date(date) == "2019-11-20" & hour(date) >= 23 | date(date) == "2019-11-21"  )

pre_debate <- pre_debate %>% select(-date, -created_at)
post_debate <- post_debate %>% select(-date, -created_at)
```

#### Sentiment Analysis
Sentiment analysis of the tweets will performed for only 5 candidates.

First we need to prep the tweets by removing all non-words such as emojis and use the sentiment analysis package for analysis. Althought the sentiment analysis packae uses 5 dictionnairies, we will only look at the results from the GI dictionnary. For the pre-debate tweets sentimeent we used all the tweets from the dataset; however for the post-debate analysis, we sampled from the dataset due to volume and processing error.   
```{r, eval=FALSE}
bs <- pre_debate %>%
      filter (BS == "TRUE")

usableText=str_replace_all(bs$text,"[^[:graph:]]", " ")

usableText <- tolower(bs$text)

usableText<- iconv(usableText, "UTF-8","ASCII",  sub="byte")

sentiments_bs = analyzeSentiment(as.character(usableText))

##

bs_post <- post_debate %>%
      filter (BS == "TRUE")

n.sample = 31603
bs_sample = bs_post[sample(1:nrow(bs_post), n.sample, replace=FALSE),]

usableText <- tolower(bs_sample$text)

usableText<- iconv(usableText, "UTF-8","ASCII",  sub="byte")

sentiments_bs_post = analyzeSentiment(as.character(usableText))

```

```{r, eval=FALSE}
kh <- pre_debate %>%
      filter (KH == "TRUE")

usableText <- tolower(kh$text)

usableText<- iconv(usableText, "UTF-8","ASCII",  sub="byte")

sentiments_kh = analyzeSentiment(as.character(usableText))

##

kh_post <- post_debate %>%
      filter (KH == "TRUE")

n.sample = 16362
kh_sample = kh_post[sample(1:nrow(kh_post), n.sample, replace=FALSE),]

usableText <- tolower(kh_sample$text)

usableText<- iconv(usableText, "UTF-8","ASCII",  sub="byte")

sentiments_kh_post = analyzeSentiment(as.character(usableText))

```

```{r, eval=FALSE}
jb <- pre_debate %>%
      filter (JB == "TRUE")

usableText <- tolower(jb$text)

usableText<- iconv(usableText, "UTF-8","ASCII",  sub="byte")

sentiments_jb = analyzeSentiment(as.character(usableText))

##
jb_post <- post_debate %>%
      filter (JB == "TRUE")

n.sample = 27477
jb_sample = jb_post[sample(1:nrow(jb_post), n.sample, replace=FALSE),]

usableText <- tolower(jb_sample$text)

usableText<- iconv(usableText, "UTF-8","ASCII",  sub="byte")

sentiments_jb_post = analyzeSentiment(as.character(usableText))

```

```{r, eval=FALSE}
ew <- pre_debate %>%
      filter (EW == "TRUE")

usableText <- tolower(ew$text)

usableText<- iconv(usableText, "UTF-8","ASCII",  sub="byte")

sentiments_ew = analyzeSentiment(as.character(usableText))

##
ew_post <- post_debate %>%
      filter (EW == "TRUE")

n.sample = 18628
ew_sample = ew_post[sample(1:nrow(ew_post), n.sample, replace=FALSE),]

usableText <- tolower(ew_sample$text)

usableText<- iconv(usableText, "UTF-8","ASCII",  sub="byte")

sentiments_ew_post = analyzeSentiment(as.character(usableText))

```

```{r, eval=FALSE}
pb <- pre_debate %>%
      filter (PB == "TRUE")

usableText <- tolower(pb$text)

usableText<- iconv(usableText, "UTF-8","ASCII",  sub="byte")

sentiments_pb = analyzeSentiment(as.character(usableText))

##

pb_post <- post_debate %>%
      filter (PB == "TRUE")

n.sample = 27242
pb_sample = pb_post[sample(1:nrow(pb_post), n.sample, replace=FALSE),]

usableText <- tolower(pb_sample$text)

usableText<- iconv(usableText, "UTF-8","ASCII",  sub="byte")

sentiments_pb_post = analyzeSentiment(as.character(usableText))
```

```{r, eval=FALSE}
pre_sent_pos <- data.frame("Candidate" = c("Biden", "Sanders", "Warren", "Harris", "Buttigieg"), 
                       "Positive" =c((sum(sentiments_jb$PositivityGI))/27477,
                                      (sum(sentiments_bs$PositivityGI))/31603,                                                                  (sum(sentiments_ew$PositivityGI))/18628,
                                     (sum(sentiments_kh$PositivityGI))/16362,
                                      (sum(sentiments_pb$PositivityGI))/27242))
```

```{r, eval=FALSE}
post_sent_pos <- data.frame("Candidate" = c("Biden", "Sanders", "Warren", "Harris", "Buttigieg"), 
                       "Positive" =c((sum(sentiments_jb_post$PositivityGI))/27477,
                                      (sum(sentiments_bs_post$PositivityGI))/31603,                                                             (sum(sentiments_ew_post$PositivityGI))/18628,
                                     (sum(sentiments_kh_post$PositivityGI))/16362,
                                      (sum(sentiments_pb_post$PositivityGI))/27242))
```

### Google Trends
This section describes gathering the Google Trends data using the package gtrends. First, we register our Google API key. Then, we pull data for each candidate from the 2 days preceding and two days following the debate (November 18 through 22). We have to pull the data in two separate blocks, because gtrends only allows us to use five search terms at a time. We limit the location of searches to the US.

```{r, eval=FALSE}
register_google(key = "AIzaSyChFy9VXwWjDdXWWxWY2Qce_cRgaE6bNVM")
res1 <- gtrends(c("Joe Biden", "Bernie Sanders", "Elizabeth Warren", "Kamala Harris", "Pete Buttigieg"), geo = "US", 
                time = "2019-11-18 2019-11-22", low_search_volume = T)

res2 <- gtrends(c("Tom Steyer", "Andrew Yang", "Cory Booker", "Amy Klobuchar", "Tulsi Gabbard"), geo = "US", 
                time = "2019-11-18 2019-11-22", low_search_volume = T)
```

#### Geocoding

Next, we compile and clean the Google Trends location data and prepare it for geocoding.

```{r, , eval=FALSE}
interest_by_location1 <- as_tibble(res1$interest_by_dma)
interest_by_location2 <- as_tibble(res2$interest_by_dma)
interest_by_location <- rbind(interest_by_location1, interest_by_location2)

locations_df <- as.data.frame(interest_by_location)
locations_df$location <- as.character(locations_df$location)
```

Then, we geocode the Google trends data.
```{r, eval=FALSE}
gc_locations <- as_tibble(mutate_geocode(locations_df, location))
```

#### Data Cleaning

Next, we categorize the Google Trends data into pre-debate and post-debate data, based on the date.
```{r, eval=FALSE}
interest_over_time1 <- as_tibble(res1$interest_over_time)
interest_over_time2 <- as_tibble(res2$interest_over_time)
interest_over_time <- rbind(interest_over_time1, interest_over_time2)

interest_over_time_pre <-
  interest_over_time %>%
  filter(date < "2019-11-19") %>%
  mutate(Pre_post="Pre-debate")

interest_over_time_post <-
  interest_over_time %>%
  filter(date > "2019-11-20") %>%
  mutate(Pre_post="Post-debate")

interest_over_time_all <- rbind(interest_over_time_pre, interest_over_time_post)
```

### Polls

Polling data was collected from RealClearPolitics, which aggregates weekly polls. We created a dataset using the RealClearPolitics average before and after the November 20 debate. Because the website changes often, and we only needed a small snapshot of the data, it was more efficient to clean the data in Excel and import to R than to use web scraping.

```{r}
polling_data <- read_excel("G:/UMD/JPSM/Fall 2019/SURV727/Project/project polling data.xlsx", sheet=1)
```

## Results

This section presents the main results.

### Data exploration

The results section may have a data exploration part, but in general the structure here depends on the specific project.

#### Twitter

Create a function to tabulate the count and proportion of tweets by candidates.

##### Create functions
```{r, eval=FALSE}
type_var  <- unlist(map(pre_debate, class))

freq_tab <- function(x) {
# make table with count and frequency
tab <- cbind(Count = table(x, useNA = "ifany"),
Prop = round(prop.table(table(x, useNA = "ifany")),
2))
# get the categories as variable and rearrenge
tab <- as.data.frame(tab) %>%
tbl_df() %>%
mutate(Cat = row.names(tab)) %>%
select(Cat, Count, Prop)
}

```

```{r, eval=FALSE}
props1 <- map(pre_debate[, type_var == "logical"], freq_tab)
props2 <- map(post_debate[, type_var == "logical"], freq_tab)

vars <- unlist(map(props1, nrow))

props_tab1 <- reduce(props1, rbind)
props_tab2 <- reduce(props2, rbind)

```

```{r, eval=FALSE}
props_tab1 <- props_tab1 %>%
mutate(Variable = rep(names(vars), vars),
       Candidate = ifelse(Variable == "BS", "Sanders",
                   ifelse(Variable == "KH", "Harris",
                   ifelse(Variable == "JB", "Biden",
                   ifelse(Variable == "EW", "Warren",
                   ifelse(Variable == "PB", "Buttigieg",
                   ifelse(Variable == "TS", "Steyer",         
                   ifelse(Variable == "AY", "Yang", 
                   ifelse(Variable == "BC", "Booker",
                   ifelse(Variable == "AK", "Klobuchar",
                   ifelse(Variable == "TG", "Gabbard", NA)))))))))))

props_tab2 <- props_tab2 %>%
mutate(Variable = rep(names(vars), vars), 
        Candidate = ifelse(Variable == "BS", "Sanders",
                   ifelse(Variable == "KH", "Harris",
                   ifelse(Variable == "JB", "Biden",
                   ifelse(Variable == "EW", "Warren",
                   ifelse(Variable == "PB", "Buttigieg",
                   ifelse(Variable == "TS", "Steyer",         
                   ifelse(Variable == "AY", "Yang", 
                   ifelse(Variable == "BC", "Booker",
                   ifelse(Variable == "AK", "Klobuchar",
                   ifelse(Variable == "TG", "Gabbard", NA)))))))))))
```

A visual of the proportion of tweets pre and post debate

##### Graphing
###### Pre-debate number of tweets

```{r, include=FALSE}
#USE THIS CHUNK TO BRING IN props_tab1 and props_tab2
load("G:/UMD/JPSM/Fall 2019/SURV727/Project/props_tab1.RData")
load("G:/UMD/JPSM/Fall 2019/SURV727/Project/props_tab2.RData")

```

```{r}
props_tab1 %>%
  filter(Cat == "TRUE") %>%
  ggplot() +
  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
    labs(x = "Democatric Party Canditates", 
       y = "Number of Tweets", 
       title = "Pre Debate candidates mentions in Tweets", 
       caption = "Source: Twiiter")

```

###### Post-debate number of tweets 
```{r}
props_tab2 %>%
  filter(Cat == "TRUE") %>%
  ggplot() +
  geom_col(mapping = aes(x = reorder(Variable, -Count), y=Count, fill = Variable)) +
    labs(x = "Democatric Party Canditates", 
       y = "Number of Tweets", 
       title = "Post Debate candidates mentions in Tweets", 
       caption = "Source: Twiiter")

```

#### Google Trends

To explore the Google Trends data, we examined the location and density of searches for each candidate. We created a map showing our results. Because it was difficult to see the results for each candidate, we created a shiny app that allows users to toggle between candidates.
```{r, include=FALSE}
#USE THIS CHUNK TO BRING IN gc_locations
load("G:/UMD/JPSM/Fall 2019/SURV727/Project/gc_locations.RData")
```

```{r}
#get map
us <- c(left = -125, bottom = 25.75, right = -67, top = 49)
us_map <- get_stamenmap(us, zoom = 5, maptype = "toner-lite")
ggmap(us_map)

#clean data for mapping
trends_map <-
  gc_locations %>%
  group_by(keyword, location) %>%
  mutate(total=sum(hits))

#generate map
ggmap(us_map) + 
  geom_point(data = trends_map, aes(x = lon, y = lat, size=total, color=keyword), alpha = 0.2)
```

We also explored the number of hits pre- and post- debate for each candidate.
```{r, include=FALSE}
#USE THIS CHUNK TO BRING IN interest_over_time_all
load("G:/UMD/JPSM/Fall 2019/SURV727/Project/interest_over_time_all.RData")
```

```{r}
interest_over_time_all %>%
  group_by(keyword, Pre_post) %>%
  summarise(total_hits=sum(hits)) %>%
  ggplot() +
  geom_col(mapping = aes(x=reorder(keyword, -total_hits), y=total_hits, fill=Pre_post), color="black")
```

#### Polling Data

For the polling data, we looked at the pre- and post-debate polling numbers for each candidate.
```{r}
polling_data %>%
  group_by(Candidate, Pre_post) %>%
  ggplot() +
    geom_col(mapping = aes(x=reorder(Candidate, -Percentage), y=Percentage, fill=Pre_post), color="black",   position="dodge")
```

### Analysis

We created a Shiny app that allows us to compare the polling, Google Trends, and Twitter sentiment data.

First, we cleaned up and combined the three data sources for use in the Shiny app.

```{r, include=FALSE}
#USE THIS CHUNK TO BRING IN pre_sent_pos and post_sent_pos
load("G:/UMD/JPSM/Fall 2019/SURV727/Project/pre_sent_pos.RData")
load("G:/UMD/JPSM/Fall 2019/SURV727/Project/post_sent_pos.RData")
```

```{r}
#clean data
gtrends <-
  interest_over_time_all %>%
  mutate(Candidate=keyword, Data="GTrends") %>%
  group_by(Candidate, Pre_post, Data) %>%
  summarise(Percentage=mean(hits))

poll <-
  polling_data %>%
  select(Candidate, Pre_post, Percentage) %>%
  mutate(Data="Polling") %>%
  group_by(Candidate, Pre_post, Data)

twitter_data <- data.frame("Candidate" = c("Joe Biden", "Bernie Sanders", "Elizabeth Warren", 
                                           "Kamala Harris", "Pete Buttigieg", "Joe Biden", 
                                           "Bernie Sanders", "Elizabeth Warren", "Kamala Harris", 
                                           "Pete Buttigieg"),                            
                           "Pre_post" =c("Pre-debate","Pre-debate","Pre-debate","Pre-debate","Pre-debate",                            "Post-debate","Post-debate","Post-debate","Post-debate","Post-debate"),
                   "Data" = c("Twitter", "Twitter","Twitter","Twitter","Twitter",
                              "Twitter","Twitter","Twitter","Twitter","Twitter"), 
                  "Percentage"=c(pre_sent_pos$Positive[1],pre_sent_pos$Positive[2],
                              pre_sent_pos$Positive[3],pre_sent_pos$Positive[4],
                              pre_sent_pos$Positive[5],post_sent_pos$Positive[1],
                              post_sent_pos$Positive[2],post_sent_pos$Positive[3],
                              post_sent_pos$Positive[4],post_sent_pos$Positive[5]))

twitter <- as_tibble(twitter_data)
twitter <-
  twitter %>%
  group_by(Candidate, Pre_post, Data) %>%
  mutate(Percentage=Percentage*100)

all_data <- rbind(poll, gtrends, twitter)
```

Then, we created a shiny app, which can be viewed by accessing the following site: ________________.
```{r}
# Define UI
ui <- fluidPage(

  # Application title
  titlePanel("2020 Democratic Primary Candidate Data"),

  # Sidebar with a dropdown
  sidebarLayout(
    sidebarPanel(
      selectInput(inputId = "Candidate",                   
                  label = "Candidate",                  
                  choices = c("Joe Biden", "Pete Buttigieg", "Kamala Harris", "Bernie Sanders", "Elizabeth Warren"),                   
                  selected = "Joe Biden"),
      selectInput(inputId = "Data",
                  label = "Data Type",
                  choices = c("Polling", "GTrends", "Twitter"),
                  selected = "Polling")
    ),

    # Show plot
    mainPanel(
      plotOutput(outputId = "graph")      
    )
  )
)

# Define server logic
server <- function(input, output) {

  output$graph <- renderPlot({
    all_data %>%
      filter(Candidate == input$Candidate, Data == input$Data) %>%
      ggplot() +
      geom_col(mapping = aes(x=Pre_post, y=Percentage, fill=input$Candidate)) +
      ylim(0,100)
  })
}

# Run the application 
shinyApp(ui = ui, server = server)

```

```{r}
# What happens here depends on the specific project
```

```{r}
# What happens here depends on the specific project
```

## Discussion

This section summarizes the results and may briefly outline advantages and limitations of the work presented.

## References

### 2019-12-06 Paper/paper-draft-Padgett-Thiam.Rmd
run paper draft

@@
 library(GGally)
+library(repmis)
+library(httr)
 ```
@@
 ```{r}
-polling_data <- read_excel("G:/UMD/JPSM/Fall 2019/SURV727/Project/project polling data.xlsx", sheet=1)
+github_link <- "https://github.com/znpadgett/surv727_padgett_thiam/raw/master/Data/Project%20polling%20data.xlsx"
+temp_file <- tempfile(fileext = ".xlsx")
+req <- GET(github_link, 
+           write_disk(path = temp_file))
+polling_data <- readxl::read_excel(temp_file)
 ```
@@
 #USE THIS CHUNK TO BRING IN props_tab1 and props_tab2
-load("G:/UMD/JPSM/Fall 2019/SURV727/Project/props_tab1.RData")
-load("G:/UMD/JPSM/Fall 2019/SURV727/Project/props_tab2.RData")
+source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/props_tab1.RData?raw=true")
+source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/props_tab2.RData?raw=true")
 
@@
 #USE THIS CHUNK TO BRING IN gc_locations
-load("G:/UMD/JPSM/Fall 2019/SURV727/Project/gc_locations.RData")
+source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/gc_locations.RData?raw=true")
 ```
@@
 #USE THIS CHUNK TO BRING IN interest_over_time_all
-load("G:/UMD/JPSM/Fall 2019/SURV727/Project/interest_over_time_all.RData")
+source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/interest_over_time_all.RData?raw=true")
 ```
@@
 #USE THIS CHUNK TO BRING IN pre_sent_pos and post_sent_pos
-load("G:/UMD/JPSM/Fall 2019/SURV727/Project/pre_sent_pos.RData")
-load("G:/UMD/JPSM/Fall 2019/SURV727/Project/post_sent_pos.RData")
+source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/post_sent_pos.RData?raw=true")
+source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/pre_sent_pos.RData?raw=true")
 ```

### 2019-12-06 Paper/paper-draft-Padgett-Thiam.Rmd
Update paper-draft-Padgett-Thiam.Rmd

@@
 We limit the location of searches to the US.
+Please note that the key here is not a real API key, for security purposes.
 
 ```{r, eval=FALSE}
-register_google(key = "AIzaSyChFy9VXwWjDdXWWxWY2Qce_cRgaE6bNVM")
+register_google(key = "XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX")
 res1 <- gtrends(c("Joe Biden", "Bernie Sanders", "Elizabeth Warren", "Kamala Harris", "Pete Buttigieg"), geo = "US", 

### 2019-12-06 Paper/paper-draft-Padgett-Thiam.Rmd
hide api keys

@@
 
-Below is our token to access the Twitter API and start collecting tweets.
+Below is our token to access the Twitter API and start collecting tweets. Note that these codes are fake, for security purposes.
 
@@
   app = "fcdd-course",
-  consumer_key = "7y8Xu96DRkBoLsdP8XbQJXTn9",
-  consumer_secret = "MCM7gcAfTJKwHks2yIRZaDZcODRQCJBusiYoZtobj4XvO7bvpV",
-  access_token = "967157671353864192-DvdUZcJN1ocpqx74YN2GwyejeIMR1Da",
-  access_secret = "KkCoMdH1vuivbWgH6IdDaDuiScNcxr389caRbhG2L2kXW"
+  consumer_key = "XXXXXXXXXXXXXXXXXXX",
+  consumer_secret = "XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX",
+  access_token = "XXXXXXXXXXXXXXXXXXX-XXXXXXXXXXXXXXXXXXX",
+  access_secret = "XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX"
 )

### 2019-12-07 Paper/paper-draft-Padgett-Thiam.Rmd
update paper code and add intro

@@
 references:
-- id: Wickham2014
-  title: Tidy Data
+- id: GayoAvello2013
+  title: A Meta-Analysis of State-of-the-Art Electoral Prediction From Twitter Data
   author:
-  - family: Wickham
-    given: Hadley
-  container-title: Journal of Statistical Software
-  volume: 59
-  issue: 10
-  page: 1-23
+  - family: Gayo-Avello
+    given: D.
+  container-title: Organization Studies
+  volume: 31
+  issue: 6
+  page: 211–248
   type: article-journal
   issued:
-    year: 2014
-- id: Baumer2017
-  title: Modern Data Science with R
+    year: 2013
+- id: Beauchamp2017
+  title: Predicting and Interpolating State-Level Polls Using Twitter Textual Data
   author:
-  - family: Baumer
-    given: Benjamin S.
-  - family: Kaplan
-    given: Daniel T.
-  - family: Horton
-    given: Nicholas J.
-  type: book
-  publisher: Chapman \& Hall/CRC Press.
+  - family: Beauchamp
+    given: N.
+  container-title: American Journal of Political Science 
+  volume: 61
+  issue: 2
+  type: article-journal
+  issued:
+    year: 2017
+- id: Gaurav2013
+  title: Leveraging Candidate Popularity on Twitter to Predict Election Outcome
+  author:
+  - family: Gaurav
+    given: M.
+  - family: Srivastava
+    given: A.
+  - family: Kumar
+    given: A.
+  - family: Miller
+    given: S.
+  container-title: Proceedings of the 7th Workshop on Social Network Mining and Analysis
+  type: article-journal
+  issued:
+    year: 2013
+- id: Kassraie2017
+  title: Election Vote Share Prediction using a Sentiment-based Fusion of Twitter Data with Google Trends and Online Polls
+  author:
+  - family: Kassraie
+    given: P.
+  - family: Modirshanechi
+    given: A.
+  - family: Aghajan
+    given: H.
+  container-title: Proceedings of the 6th International Conference on Data Science, Technology and Applications
+  type: article-journal
+  issued:
+    year: 2017
+- id: Salunkhe2017
+  title: Twitter Based Election Prediction and Analysis
+  author:
+  - family: Salunkhe
+    given: P.
+  - family: Deshmukh
+    given: S.
+  container-title: International Research Journal of Engineering and Technology
+  volume: 4
+  issue: 10
+  type: article-journal
   issued:
@@
 TO DO:
-- write intro, results, and discussion sections
-- save the following datasets to github and write code in designated chunks to bring them in:
-    props_tab1
-    props_tab2
-    gc_locations
-    interest_over_time_all
-    pre_sent_pos
-    post_sent_pos
+- write results, and discussion sections
 - create presentation
@@
 
-This section outlines the research idea. We can also cite related work here [@Wickham2014; @Baumer2017].
+Twitter and Google Trends are becoming increasingly popular tools for social science researchers.
+They represent an easily accessible source of large amounts of data, which has become advantageous as survey response rates decline and costs rise.
+Researchers interested in predicting election results have begun looking to Twitter data to replace or supplement traditional election polls, with mixed results [@GayoAvello2013].
 
-Note that compiled term paper (the PDF) is supposed to be more text-centered than the RMarkdown documents we used in class, i.e.
-the text sections are more detailed and big or redundant code chunks can be hidden.
+Recently, there have been studies using sentiment analysis of Twitter data to predict election outcomes in India [@Salunkhe2017], to predict state-level polling results in the U.S.
+[@Beauchamp2017], and to predict the winners of three presidential elections in Latin America [@Gaurav2013].
+Beauchamp (2017) found that Twitter data may be useful in making state-level campaign strategy decisions.
+Additionally, a recent study used Google Trends and Twitter data to predict the 2016 U.S.
+election outcomes with only 1% error [@Kassraie2017].
+
+We are interested in whether Twitter data and Google trends data could be used to supplement polling results, by providing real-time information to candidates while they wait for polling data to come in.
+For example, candidates may be interested in understanding how public opinion has shifted immediately after a debate in order to run a more agile campaign.
+This project is an exploratory analysis of Twitter and Google Trends data to see if pre- and post-debate polling data during the 2020 U.S.
+Democratic primary election aligns with these real-time sources.
 
@@
 
-```{r, eval=FALSE}
+```{r, eval=FALSE, tidy=TRUE}
 
@@
 In that case, the tweet will be found in the each of those candidate dataset.
+The code below exemplifies this step of the cleaning process.
 
-```{r, eval=FALSE}
+```{r, eval=FALSE, tidy=TRUE}
 tweets$BS <-(str_detect(tweets$text, regex("#Sanders|@BernieSanders", ignore_case = TRUE)))
@@
 
-```{r, eval=FALSE}
+```{r, eval=FALSE, include=FALSE}
 df1$BS <-(str_detect(df1$text, regex("#Sanders|@BernieSanders", ignore_case = TRUE)))
@@
 
-```{r, eval=FALSE}
+```{r, eval=FALSE, include=FALSE}
 df2$BS <-(str_detect(df2$text, regex("#Sanders|@BernieSanders", ignore_case = TRUE)))
@@
 Note that tweets during the debate( 9 - 11 p.m are ignored)
-```{r, eval=FALSE}
+```{r, eval=FALSE, tidy=TRUE}
 pre_debate <- tweets %>%
@@
 For the pre-debate tweets sentimeent we used all the tweets from the dataset; however for the post-debate analysis, we sampled from the dataset due to volume and processing error.
+The code below exemplifies this process.
 ```{r, eval=FALSE}
@@
 
-##
+```
 
+```{r, eval=FALSE, include=FALSE}
 bs_post <- post_debate %>%
@@
 
-```{r, eval=FALSE}
+```{r, eval=FALSE, include=FALSE}
 kh <- pre_debate %>%
@@
 
-```{r, eval=FALSE}
+```{r, eval=FALSE, include=FALSE}
 jb <- pre_debate %>%
@@
 
-```{r, eval=FALSE}
+```{r, eval=FALSE, include=FALSE}
 ew <- pre_debate %>%
@@
 
-```{r, eval=FALSE}
+```{r, eval=FALSE, include=FALSE}
 pb <- pre_debate %>%
@@
 
-```{r, eval=FALSE}
+```{r, eval=FALSE, tidy=TRUE}
 pre_sent_pos <- data.frame("Candidate" = c("Biden", "Sanders", "Warren", "Harris", "Buttigieg"), 
@@
 
-```{r, eval=FALSE}
+```{r, eval=FALSE, include=FALSE}
 post_sent_pos <- data.frame("Candidate" = c("Biden", "Sanders", "Warren", "Harris", "Buttigieg"), 
@@
 
-```{r, eval=FALSE}
+```{r, eval=FALSE, tidy=TRUE}
 register_google(key = "XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX")
@@
 
-```{r}
+```{r, tidy=TRUE}
 github_link <- "https://github.com/znpadgett/surv727_padgett_thiam/raw/master/Data/Project%20polling%20data.xlsx"
@@
 
-```{r}
+```{r, message=FALSE, warning=FALSE, results="hide", fig.show="hide"}
 #get map
@@
 ggmap(us_map) 
+```
 
+```{r, message=FALSE, warning=FALSE}
 #clean data for mapping
@@
 
-```{r}
+```{r, tidy=TRUE}
 interest_over_time_all %>%
@@
 For the polling data, we looked at the pre- and post-debate polling numbers for each candidate.
-```{r}
+```{r, tidy=TRUE}
 polling_data %>%
@@
 
-```{r}
+```{r, tidy=TRUE, warning=FALSE, message=FALSE}
 #clean data
@@
 Then, we created a shiny app, which can be viewed by accessing the following site: ________________.
-```{r}
+```{r, eval=FALSE, tidy=TRUE}
 # Define UI

### 2019-12-07 Paper/paper-draft-Padgett-Thiam.Rmd
update paper and rmd file
updated formatting of pdf, figure titles, figure formatting

@@
 date: "`r Sys.Date()`"
+fontsize: 12pt
+text-align: left
 output:
@@
 
-```{r, include = FALSE}
+```{r, echo = FALSE, include=FALSE}
 library(knitr)
@@
 library(httr)
+```
+
+```{r, message="FALSE", warning=FALSE, results="hide", include=FALSE}
+opts_chunk$set(tidy.opts=list(width=60),tidy=TRUE)
 ```
@@
 
-dem <- search_tweets("#democrats OR #candidates OR #election2020 OR #BIDEN OR #sanders OR #warren OR #harris 
-                     OR #buttigieg OR #steyer OR #yang OR #booker OR #klobuchar OR #gabbard   
-                     OR @KamalaHarris OR @JoeBiden OR @BernieSanders OR @ewarren OR @PeteButtigieg 
-                     OR @TomSteyer OR @AndrewYang OR @BookerCory OR @amyklobuchar OR @TulsiGabbard ",  since='2019-11-20', until='2019-11-21', n= 500000,  retryonratelimit = TRUE, verbose = TRUE)
+dem <- search_tweets("#democrats OR #candidates OR #election2020 OR #BIDEN 
+                     OR #sanders OR #warren OR #harris 
+                     OR #buttigieg OR #steyer OR #yang OR #booker 
+                     OR #klobuchar OR #gabbard   
+                     OR @KamalaHarris OR @JoeBiden OR @BernieSanders 
+                     OR @ewarren OR @PeteButtigieg 
+                     OR @TomSteyer OR @AndrewYang OR @BookerCory 
+                     OR @amyklobuchar OR @TulsiGabbard ",  since='2019-11-20', 
+                     until='2019-11-21', n= 500000,  
+                     retryonratelimit = TRUE, verbose = TRUE)
 ```
@@
 df1 <- df1 %>%
-      mutate( ukraine = (str_detect(df1$text, regex("Ukraine", ignore_case = TRUE)))) %>%
+      mutate( ukraine = (str_detect(df1$text, 
+                                    regex("Ukraine", 
+                                          ignore_case = TRUE)))) %>%
       filter(ukraine=="FALSE") %>%
@@
 df2 <- df2 %>%
-      mutate( ukraine = (str_detect(df2$text, regex("Ukraine", ignore_case = TRUE)))) %>%
+      mutate( ukraine = (str_detect(df2$text, 
+                                    regex("Ukraine", 
+                                          ignore_case = TRUE)))) %>%
       filter(ukraine=="FALSE") %>%
@@
 ```{r, eval=FALSE, tidy=TRUE}
-tweets$BS <-(str_detect(tweets$text, regex("#Sanders|@BernieSanders", ignore_case = TRUE)))
-tweets$KH <-(str_detect(tweets$text, regex("#harris |@KamalaHarris",  ignore_case = TRUE)))
-tweets$JB <-(str_detect(tweets$text, regex("#biden |@JoeBiden", ignore_case = TRUE)))
-tweets$EW <-(str_detect(tweets$text, regex("#warren |@ewarren", ignore_case = TRUE)))
-tweets$PB <-(str_detect(tweets$text, regex("#buttigieg|@PeteButtigieg", ignore_case = TRUE)))
-tweets$TS <-(str_detect(tweets$text, regex("#steyer | @TomSteyer", ignore_case = TRUE)))
-tweets$AY <-(str_detect(tweets$text, regex("#yang| @AndrewYang", ignore_case = TRUE)))
-tweets$BC <-(str_detect(tweets$text, regex("#booker | @BookerCory", ignore_case = TRUE)))
-tweets$AK <-(str_detect(tweets$text, regex("#klobuchar | @amyklobuchar", ignore_case = TRUE)))
-tweets$TG <-(str_detect(tweets$text, regex("#gabbard |@TulsiGabbard", ignore_case = TRUE)))
-
+tweets$BS <-(str_detect(tweets$text, 
+                        regex("#Sanders|@BernieSanders", 
+                              ignore_case = TRUE)))
+tweets$KH <-(str_detect(tweets$text, 
+                        regex("#harris |@KamalaHarris",  
+                              ignore_case = TRUE)))
+tweets$JB <-(str_detect(tweets$text, 
+                        regex("#biden |@JoeBiden", 
+                              ignore_case = TRUE)))
+tweets$EW <-(str_detect(tweets$text, 
+                        regex("#warren |@ewarren", 
+                              ignore_case = TRUE)))
+tweets$PB <-(str_detect(tweets$text, 
+                        regex("#buttigieg|@PeteButtigieg", 
+                              ignore_case = TRUE)))
+tweets$TS <-(str_detect(tweets$text, 
+                        regex("#steyer | @TomSteyer", 
+                              ignore_case = TRUE)))
+tweets$AY <-(str_detect(tweets$text, 
+                        regex("#yang| @AndrewYang", 
+                              ignore_case = TRUE)))
+tweets$BC <-(str_detect(tweets$text, 
+                        regex("#booker | @BookerCory", 
+                              ignore_case = TRUE)))
+tweets$AK <-(str_detect(tweets$text, 
+                        regex("#klobuchar | @amyklobuchar", 
+                              ignore_case = TRUE)))
+tweets$TG <-(str_detect(tweets$text, 
+                        regex("#gabbard |@TulsiGabbard", 
+                              ignore_case = TRUE)))
 ```
@@
 post_debate <- tweets %>%
-              filter(date(date) == "2019-11-20" & hour(date) >= 23 | date(date) == "2019-11-21"  )
+              filter(date(date) == "2019-11-20" & hour(date) >= 23 | 
+                       date(date) == "2019-11-21"  )
 
@@
 ```{r, eval=FALSE, tidy=TRUE}
-pre_sent_pos <- data.frame("Candidate" = c("Biden", "Sanders", "Warren", "Harris", "Buttigieg"), 
+pre_sent_pos <- data.frame("Candidate" = c("Biden", 
+                                           "Sanders", 
+                                           "Warren", 
+                                           "Harris", 
+                                           "Buttigieg"), 
                        "Positive" =c((sum(sentiments_jb$PositivityGI))/27477,
@@
 register_google(key = "XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX")
-res1 <- gtrends(c("Joe Biden", "Bernie Sanders", "Elizabeth Warren", "Kamala Harris", "Pete Buttigieg"), geo = "US", 
+res1 <- gtrends(c("Joe Biden", "Bernie Sanders", 
+                  "Elizabeth Warren", "Kamala Harris", 
+                  "Pete Buttigieg"), geo = "US", 
                 time = "2019-11-18 2019-11-22", low_search_volume = T)
 
-res2 <- gtrends(c("Tom Steyer", "Andrew Yang", "Cory Booker", "Amy Klobuchar", "Tulsi Gabbard"), geo = "US", 
+res2 <- gtrends(c("Tom Steyer", "Andrew Yang", "Cory Booker", 
+                  "Amy Klobuchar", "Tulsi Gabbard"), geo = "US", 
                 time = "2019-11-18 2019-11-22", low_search_volume = T)
@@
 
-```{r}
+```{r, fig.cap="Pre-debate Mentions in Tweets, by Candidate"}
 props_tab1 %>%
@@
        y = "Number of Tweets", 
-       title = "Pre Debate candidates mentions in Tweets", 
        caption = "Source: Twiiter")
@@
 ###### Post-debate number of tweets 
-```{r}
+```{r, fig.cap="Post-debate Mentions in Tweets, by Candidate"}
 props_tab2 %>%
@@
        y = "Number of Tweets", 
-       title = "Post Debate candidates mentions in Tweets", 
        caption = "Source: Twiiter")
@@
 We created a map showing our results.
-Because it was difficult to see the results for each candidate, we created a shiny app that allows users to toggle between candidates.
+Because it was difficult to see the results for each candidate overlaid on one map, we added a facet wrap to show each individual candidate.
 ```{r, include=FALSE}
@@
 
-```{r, message=FALSE, warning=FALSE}
+```{r, message=FALSE, warning=FALSE, fig.height=10, fig.width=12, fig.cap="Map of Google Trends Hits, by Candidate"}
 #clean data for mapping
@@
   group_by(keyword, location) %>%
-  mutate(total=sum(hits))
+  mutate("Hits"=sum(hits), Candidate=keyword)
 
@@
 ggmap(us_map) + 
-  geom_point(data = trends_map, aes(x = lon, y = lat, size=total, color=keyword), alpha = 0.2)
+  geom_point(data = trends_map, aes(x = lon, y = lat, size=Hits, color=Candidate), 
+             alpha = 0.2) +
+  theme(axis.line=element_blank(),axis.text.x=element_blank(),
+          axis.text.y=element_blank(),axis.ticks=element_blank(),
+          axis.title.x=element_blank(),
+          axis.title.y=element_blank()) +
+  facet_wrap("Candidate", shrink=FALSE)
 ```
@@
 
-```{r, tidy=TRUE}
+```{r, tidy=TRUE, fig.cap="Pre- and Post-debate Google Trends Data, by Candidate"}
+interest_over_time_all$Pre_post <- factor(interest_over_time_all$Pre_post, 
+                                          levels = c("Pre-debate", "Post-debate"))
+
 interest_over_time_all %>%
   group_by(keyword, Pre_post) %>%
-  summarise(total_hits=sum(hits)) %>%
+  summarise(avg_hits=mean(hits)) %>%
   ggplot() +
-  geom_col(mapping = aes(x=reorder(keyword, -total_hits), y=total_hits, fill=Pre_post), color="black")
+  geom_col(mapping = aes(x=reorder(keyword, -avg_hits), 
+                         y=avg_hits, fill=Pre_post), color="black", 
+           position="dodge") +
+  xlab("Candidate") + ylab("Hits") +
+  scale_fill_discrete(name = "Timeframe") +
+  theme(axis.text.x = element_text(angle=35))
+
 ```
@@
 For the polling data, we looked at the pre- and post-debate polling numbers for each candidate.
-```{r, tidy=TRUE}
+```{r, tidy=TRUE, fig.cap="Pre- and Post-debate Polling Data, by Candidate"}
+polling_data$Pre_post <- factor(polling_data$Pre_post, levels = c("Pre-debate", "Post-debate"))
+
 polling_data %>%
   group_by(Candidate, Pre_post) %>%
+  filter(Candidate!="Bennet", Candidate!="Bloomberg") %>%
   ggplot() +
-    geom_col(mapping = aes(x=reorder(Candidate, -Percentage), y=Percentage, fill=Pre_post), color="black",   position="dodge")
+    geom_col(mapping = aes(x=reorder(Candidate, -Percentage), y=Percentage, 
+                           fill=Pre_post), color="black",   position="dodge") +
+  xlab("Candidate") + ylab("Percentage") +
+  scale_fill_discrete(name = "Timeframe") +
+  theme(axis.text.x = element_text(angle=35))
 ```
@@
 
-twitter_data <- data.frame("Candidate" = c("Joe Biden", "Bernie Sanders", "Elizabeth Warren", 
-                                           "Kamala Harris", "Pete Buttigieg", "Joe Biden", 
-                                           "Bernie Sanders", "Elizabeth Warren", "Kamala Harris", 
-                                           "Pete Buttigieg"),                            
-                           "Pre_post" =c("Pre-debate","Pre-debate","Pre-debate","Pre-debate","Pre-debate",                            "Post-debate","Post-debate","Post-debate","Post-debate","Post-debate"),
+twitter_data <- data.frame("Candidate" = c("Joe Biden", "Bernie Sanders", 
+                                           "Elizabeth Warren", "Kamala Harris", 
+                                           "Pete Buttigieg", "Joe Biden", 
+                                           "Bernie Sanders", "Elizabeth Warren", 
+                                           "Kamala Harris", "Pete Buttigieg"),                            
+                           "Pre_post" =c("Pre-debate","Pre-debate",
+                                         "Pre-debate","Pre-debate","Pre-debate",                            "Post-debate","Post-debate","Post-debate","Post-debate","Post-debate"),
                    "Data" = c("Twitter", "Twitter","Twitter","Twitter","Twitter",
@@
 all_data <- rbind(poll, gtrends, twitter)
+
+all_data$Pre_post <- factor(all_data$Pre_post, levels = c("Pre-debate", 
+                                                          "Post-debate"))
 ```
 
-Then, we created a shiny app, which can be viewed by accessing the following site: ________________.
+Then, we created a shiny app, which can be viewed by running the following code:
 ```{r, eval=FALSE, tidy=TRUE}
@@
                   label = "Candidate",                  
-                  choices = c("Joe Biden", "Pete Buttigieg", "Kamala Harris", "Bernie Sanders", "Elizabeth Warren"),                   
+                  choices = c("Joe Biden", "Pete Buttigieg", "Kamala Harris", 
+                              "Bernie Sanders", "Elizabeth Warren"),                   
                   selected = "Joe Biden"),
@@
       geom_col(mapping = aes(x=Pre_post, y=Percentage, fill=input$Candidate)) +
-      ylim(0,100)
+      ylim(0,100) +
+      xlab("Timeframe") + ylab("Percentage") +
+      theme(legend.position = "none")
   })

### 2019-12-07 Paper/paper-draft-Padgett-Thiam.Rmd
added paper title and authors

@@
 ---
-title: "Fundamentals of Computing and Data Display"
-subtitle: "Term paper template"
-author: "Author"
+title: "Pre- and Post-Debate Democratic Primary Data: Twitter, Google Trends, and Polls"
+subtitle: "Fundamentals of Computing and Data Display, Fall 2019"
+author: "Zoe Padgett and Fatou Thiam"
 date: "`r Sys.Date()`"

### 2019-12-08 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
add presentation draft

--- 2019-12-07 Paper/paper-draft-Padgett-Thiam.Rmd
@@
 ---
-title: "Fundamentals of Computing and Data Display"
-subtitle: "Term paper template"
-author: "Author"
-date: "`r Sys.Date()`"
-fontsize: 12pt
-text-align: left
-output:
-  pdf_document:
-    toc: yes
-    df_print: kable
-references:
-- id: GayoAvello2013
-  title: A Meta-Analysis of State-of-the-Art Electoral Prediction From Twitter Data
-  author:
-  - family: Gayo-Avello
-    given: D.
-  container-title: Organization Studies
-  volume: 31
-  issue: 6
-  page: 211–248
-  type: article-journal
-  issued:
-    year: 2013
-- id: Beauchamp2017
-  title: Predicting and Interpolating State-Level Polls Using Twitter Textual Data
-  author:
-  - family: Beauchamp
-    given: N.
-  container-title: American Journal of Political Science 
-  volume: 61
-  issue: 2
-  type: article-journal
-  issued:
-    year: 2017
-- id: Gaurav2013
-  title: Leveraging Candidate Popularity on Twitter to Predict Election Outcome
-  author:
-  - family: Gaurav
-    given: M.
-  - family: Srivastava
-    given: A.
-  - family: Kumar
-    given: A.
-  - family: Miller
-    given: S.
-  container-title: Proceedings of the 7th Workshop on Social Network Mining and Analysis
-  type: article-journal
-  issued:
-    year: 2013
-- id: Kassraie2017
-  title: Election Vote Share Prediction using a Sentiment-based Fusion of Twitter Data with Google Trends and Online Polls
-  author:
-  - family: Kassraie
-    given: P.
-  - family: Modirshanechi
-    given: A.
-  - family: Aghajan
-    given: H.
-  container-title: Proceedings of the 6th International Conference on Data Science, Technology and Applications
-  type: article-journal
-  issued:
-    year: 2017
-- id: Salunkhe2017
-  title: Twitter Based Election Prediction and Analysis
-  author:
-  - family: Salunkhe
-    given: P.
-  - family: Deshmukh
-    given: S.
-  container-title: International Research Journal of Engineering and Technology
-  volume: 4
-  issue: 10
-  type: article-journal
-  issued:
-    year: 2017
+title: "Pre- and Post-Debate Democratic Primary Data: Twitter, Google Trends, and Polls"
+subtitle: "Fundamentals of Computing and Data Display, Fall 2019"
+author: "Zoe Padgett and Fatou Thiam"
+date: "12/9/2019"
+output: ioslides_presentation
+runtime: shiny
 ---
 
-TO DO:
-- write results, and discussion sections
-- create presentation
-
-```{r, echo = FALSE, include=FALSE}
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE)
 library(knitr)
@@
 
-```{r, message="FALSE", warning=FALSE, results="hide", include=FALSE}
-opts_chunk$set(tidy.opts=list(width=60),tidy=TRUE)
-```
+## Overview
 
-## Introduction
+This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
 
-Twitter and Google Trends are becoming increasingly popular tools for social science researchers.
-They represent an easily accessible source of large amounts of data, which has become advantageous as survey response rates decline and costs rise.
-Researchers interested in predicting election results have begun looking to Twitter data to replace or supplement traditional election polls, with mixed results [@GayoAvello2013].
+When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
 
-Recently, there have been studies using sentiment analysis of Twitter data to predict election outcomes in India [@Salunkhe2017], to predict state-level polling results in the U.S.
-[@Beauchamp2017], and to predict the winners of three presidential elections in Latin America [@Gaurav2013].
-Beauchamp (2017) found that Twitter data may be useful in making state-level campaign strategy decisions.
-Additionally, a recent study used Google Trends and Twitter data to predict the 2016 U.S.
-election outcomes with only 1% error [@Kassraie2017].
+## Twitter Data
 
-We are interested in whether Twitter data and Google trends data could be used to supplement polling results, by providing real-time information to candidates while they wait for polling data to come in.
-For example, candidates may be interested in understanding how public opinion has shifted immediately after a debate in order to run a more agile campaign.
-This project is an exploratory analysis of Twitter and Google Trends data to see if pre- and post-debate polling data during the 2020 U.S.
-Democratic primary election aligns with these real-time sources.
+- Bullet 1
+- Bullet 2
+- Bullet 3
 
-## Data
+## Google Trends Data
 
-This section describes the data sources and the data gathering process.
+- Used gtrends package to pull Google Trends data for each candidate before and after the debate
+- Generated maps for each candidate to see the geographic distribution of searches
+- Graphed the search popularity of each candidate pre- and post-debate
 
-### Twitter
-
-Below is our token to access the Twitter API and start collecting tweets. Note that these codes are fake, for security purposes.
-
-```{r, eval=FALSE}
-create_token(
-  app = "fcdd-course",
-  consumer_key = "XXXXXXXXXXXXXXXXXXX",
-  consumer_secret = "XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX",
-  access_token = "XXXXXXXXXXXXXXXXXXX-XXXXXXXXXXXXXXXXXXX",
-  access_secret = "XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX"
-)
-```
-
-#### Quering Tweets
-
-Using the search_tweets function in the rtweets package, we will be quering tweets with the keywords specified below.
-We limited our tweets pool to November 20th and November 21st.
-The reasonning behind this is to get a feel post and pre debate.
-
-```{r, eval=FALSE, tidy=TRUE}
-
-dem <- search_tweets("#democrats OR #candidates OR #election2020 OR #BIDEN 
-                     OR #sanders OR #warren OR #harris 
-                     OR #buttigieg OR #steyer OR #yang OR #booker 
-                     OR #klobuchar OR #gabbard   
-                     OR @KamalaHarris OR @JoeBiden OR @BernieSanders 
-                     OR @ewarren OR @PeteButtigieg 
-                     OR @TomSteyer OR @AndrewYang OR @BookerCory 
-                     OR @amyklobuchar OR @TulsiGabbard ",  since='2019-11-20', 
-                     until='2019-11-21', n= 500000,  
-                     retryonratelimit = TRUE, verbose = TRUE)
-```
-
-#### Data Cleaning
-
-Even after we specify the keywords, we know that we would still get irrelevants tweets mainly with the Ukraine issue at the time of pulling. We removed all tweets that had the word "Ukraine" in it.
-
-```{r, eval=FALSE}
-myvars <- c("text", "location", "created_at")
-df1 <- dem[myvars]
-df2 <- dem2[myvars]
-```
-
-```{r, eval=FALSE}
-df1 <- df1 %>%
-      mutate( ukraine = (str_detect(df1$text, 
-                                    regex("Ukraine", 
-                                          ignore_case = TRUE)))) %>%
-      filter(ukraine=="FALSE") %>%
-      select(-ukraine)
-
-df2 <- df2 %>%
-      mutate( ukraine = (str_detect(df2$text, 
-                                    regex("Ukraine", 
-                                          ignore_case = TRUE)))) %>%
-      filter(ukraine=="FALSE") %>%
-      select(-ukraine)
-```
-
-```{r, eval=FALSE}
-tweets <- rbind(df1, df2)
-
-```
-
-Next, we seperate the tweets by candidates in order to do the analysis at the candidate level.
-It's important to note that one tweets can be addressed to multiple candidates.
-In that case, the tweet will be found in the each of those candidate dataset.
-The code below exemplifies this step of the cleaning process.
-
-```{r, eval=FALSE, tidy=TRUE}
-tweets$BS <-(str_detect(tweets$text, 
-                        regex("#Sanders|@BernieSanders", 
-                              ignore_case = TRUE)))
-tweets$KH <-(str_detect(tweets$text, 
-                        regex("#harris |@KamalaHarris",  
-                              ignore_case = TRUE)))
-tweets$JB <-(str_detect(tweets$text, 
-                        regex("#biden |@JoeBiden", 
-                              ignore_case = TRUE)))
-tweets$EW <-(str_detect(tweets$text, 
-                        regex("#warren |@ewarren", 
-                              ignore_case = TRUE)))
-tweets$PB <-(str_detect(tweets$text, 
-                        regex("#buttigieg|@PeteButtigieg", 
-                              ignore_case = TRUE)))
-tweets$TS <-(str_detect(tweets$text, 
-                        regex("#steyer | @TomSteyer", 
-                              ignore_case = TRUE)))
-tweets$AY <-(str_detect(tweets$text, 
-                        regex("#yang| @AndrewYang", 
-                              ignore_case = TRUE)))
-tweets$BC <-(str_detect(tweets$text, 
-                        regex("#booker | @BookerCory", 
-                              ignore_case = TRUE)))
-tweets$AK <-(str_detect(tweets$text, 
-                        regex("#klobuchar | @amyklobuchar", 
-                              ignore_case = TRUE)))
-tweets$TG <-(str_detect(tweets$text, 
-                        regex("#gabbard |@TulsiGabbard", 
-                              ignore_case = TRUE)))
-```
-
-```{r, eval=FALSE, include=FALSE}
-df1$BS <-(str_detect(df1$text, regex("#Sanders|@BernieSanders", ignore_case = TRUE)))
-df1$KH <-(str_detect(df1$text, regex("#harris |@KamalaHarris",  ignore_case = TRUE)))
-df1$JB <-(str_detect(df1$text, regex("#biden |@JoeBiden", ignore_case = TRUE)))
-df1$EW <-(str_detect(df1$text, regex("#warren |@ewarren", ignore_case = TRUE)))
-df1$PB <-(str_detect(df1$text, regex("#buttigieg|@PeteButtigieg", ignore_case = TRUE)))
-df1$TS <-(str_detect(df1$text, regex("#steyer | @TomSteyer", ignore_case = TRUE)))
-df1$AY <-(str_detect(df1$text, regex("#yang| @AndrewYang", ignore_case = TRUE)))
-df1$BC <-(str_detect(df1$text, regex("#booker | @BookerCory", ignore_case = TRUE)))
-df1$AK <-(str_detect(df1$text, regex("#klobuchar | @amyklobuchar", ignore_case = TRUE)))
-df1$TG <-(str_detect(df1$text, regex("#gabbard |@TulsiGabbard", ignore_case = TRUE)))
-
-```
-
-```{r, eval=FALSE, include=FALSE}
-df2$BS <-(str_detect(df2$text, regex("#Sanders|@BernieSanders", ignore_case = TRUE)))
-df2$KH <-(str_detect(df2$text, regex("#harris |@KamalaHarris",  ignore_case = TRUE)))
-df2$JB <-(str_detect(df2$text, regex("#biden |@JoeBiden", ignore_case = TRUE)))
-df2$EW <-(str_detect(df2$text, regex("#warren |@ewarren", ignore_case = TRUE)))
-df2$PB <-(str_detect(df2$text, regex("#buttigieg|@PeteButtigieg", ignore_case = TRUE)))
-df2$TS <-(str_detect(df2$text, regex("#steyer | @TomSteyer", ignore_case = TRUE)))
-df2$AY <-(str_detect(df2$text, regex("#yang| @AndrewYang", ignore_case = TRUE)))
-df2$BC <-(str_detect(df2$text, regex("#booker | @BookerCory", ignore_case = TRUE)))
-df2$AK <-(str_detect(df2$text, regex("#klobuchar | @amyklobuchar", ignore_case = TRUE)))
-df2$TG <-(str_detect(df2$text, regex("#gabbard |@TulsiGabbard", ignore_case = TRUE)))
-
-```
-
-Here we reformat the created_at column as a date & time variable in order to seperate the tweets in two groups : post and pre debate.
-```{r, eval=FALSE}
-tweets <- tweets %>%
-  mutate( date= as.POSIXct(created_at, tryFormats = c("%Y-%m-%d %H:%M:%OS")))
-
-df1 <- df1 %>%
-    mutate( date= as.POSIXct(created_at, tryFormats = c("%Y-%m-%d %H:%M:%OS")))
-
-df2 <- df2 %>%
-    mutate( date= as.POSIXct(created_at, tryFormats = c("%Y-%m-%d %H:%M:%OS")))
-
-```
-
-All the tweets received before 9 p.m.
-on November 20th are accounted for in the pre-debate dataset and all tweets from 11 p.m.
-on November 20th to the next day are in the post-debate dataset.
-Note that tweets during the debate( 9 - 11 p.m are ignored)
-```{r, eval=FALSE, tidy=TRUE}
-pre_debate <- tweets %>%
-              filter(date(date) == "2019-11-20" & hour(date) < 21 )
-
-post_debate <- tweets %>%
-              filter(date(date) == "2019-11-20" & hour(date) >= 23 | 
-                       date(date) == "2019-11-21"  )
-
-pre_debate <- pre_debate %>% select(-date, -created_at)
-post_debate <- post_debate %>% select(-date, -created_at)
-```
-
-#### Sentiment Analysis
-Sentiment analysis of the tweets will performed for only 5 candidates.
-
-First we need to prep the tweets by removing all non-words such as emojis and use the sentiment analysis package for analysis.
-Althought the sentiment analysis packae uses 5 dictionnairies, we will only look at the results from the GI dictionnary.
-For the pre-debate tweets sentimeent we used all the tweets from the dataset; however for the post-debate analysis, we sampled from the dataset due to volume and processing error.
-The code below exemplifies this process.
-```{r, eval=FALSE}
-bs <- pre_debate %>%
-      filter (BS == "TRUE")
-
-usableText=str_replace_all(bs$text,"[^[:graph:]]", " ")
-
-usableText <- tolower(bs$text)
-
-usableText<- iconv(usableText, "UTF-8","ASCII",  sub="byte")
-
-sentiments_bs = analyzeSentiment(as.character(usableText))
-
-```
-
-```{r, eval=FALSE, include=FALSE}
-bs_post <- post_debate %>%
-      filter (BS == "TRUE")
-
-n.sample = 31603
-bs_sample = bs_post[sample(1:nrow(bs_post), n.sample, replace=FALSE),]
-
-usableText <- tolower(bs_sample$text)
-
-usableText<- iconv(usableText, "UTF-8","ASCII",  sub="byte")
-
-sentiments_bs_post = analyzeSentiment(as.character(usableText))
-
-```
-
-```{r, eval=FALSE, include=FALSE}
-kh <- pre_debate %>%
-      filter (KH == "TRUE")
-
-usableText <- tolower(kh$text)
-
-usableText<- iconv(usableText, "UTF-8","ASCII",  sub="byte")
-
-sentiments_kh = analyzeSentiment(as.character(usableText))
-
-##
-
-kh_post <- post_debate %>%
-      filter (KH == "TRUE")
-
-n.sample = 16362
-kh_sample = kh_post[sample(1:nrow(kh_post), n.sample, replace=FALSE),]
-
-usableText <- tolower(kh_sample$text)
-
-usableText<- iconv(usableText, "UTF-8","ASCII",  sub="byte")
-
-sentiments_kh_post = analyzeSentiment(as.character(usableText))
-
-```
-
-```{r, eval=FALSE, include=FALSE}
-jb <- pre_debate %>%
-      filter (JB == "TRUE")
-
-usableText <- tolower(jb$text)
-
-usableText<- iconv(usableText, "UTF-8","ASCII",  sub="byte")
-
-sentiments_jb = analyzeSentiment(as.character(usableText))
-
-##
-jb_post <- post_debate %>%
-      filter (JB == "TRUE")
-
-n.sample = 27477
-jb_sample = jb_post[sample(1:nrow(jb_post), n.sample, replace=FALSE),]
-
-usableText <- tolower(jb_sample$text)
-
-usableText<- iconv(usableText, "UTF-8","ASCII",  sub="byte")
-
-sentiments_jb_post = analyzeSentiment(as.character(usableText))
-
-```
-
-```{r, eval=FALSE, include=FALSE}
-ew <- pre_debate %>%
-      filter (EW == "TRUE")
-
-usableText <- tolower(ew$text)
-
-usableText<- iconv(usableText, "UTF-8","ASCII",  sub="byte")
-
-sentiments_ew = analyzeSentiment(as.character(usableText))
-
-##
-ew_post <- post_debate %>%
-      filter (EW == "TRUE")
-
-n.sample = 18628
-ew_sample = ew_post[sample(1:nrow(ew_post), n.sample, replace=FALSE),]
-
-usableText <- tolower(ew_sample$text)
-
-usableText<- iconv(usableText, "UTF-8","ASCII",  sub="byte")
-
-sentiments_ew_post = analyzeSentiment(as.character(usableText))
-
-```
-
-```{r, eval=FALSE, include=FALSE}
-pb <- pre_debate %>%
-      filter (PB == "TRUE")
-
-usableText <- tolower(pb$text)
-
-usableText<- iconv(usableText, "UTF-8","ASCII",  sub="byte")
-
-sentiments_pb = analyzeSentiment(as.character(usableText))
-
-##
-
-pb_post <- post_debate %>%
-      filter (PB == "TRUE")
-
-n.sample = 27242
-pb_sample = pb_post[sample(1:nrow(pb_post), n.sample, replace=FALSE),]
-
-usableText <- tolower(pb_sample$text)
-
-usableText<- iconv(usableText, "UTF-8","ASCII",  sub="byte")
-
-sentiments_pb_post = analyzeSentiment(as.character(usableText))
-```
-
-```{r, eval=FALSE, tidy=TRUE}
-pre_sent_pos <- data.frame("Candidate" = c("Biden", 
-                                           "Sanders", 
-                                           "Warren", 
-                                           "Harris", 
-                                           "Buttigieg"), 
-                       "Positive" =c((sum(sentiments_jb$PositivityGI))/27477,
-                                      (sum(sentiments_bs$PositivityGI))/31603,                                                                  (sum(sentiments_ew$PositivityGI))/18628,
-                                     (sum(sentiments_kh$PositivityGI))/16362,
-                                      (sum(sentiments_pb$PositivityGI))/27242))
-```
-
-```{r, eval=FALSE, include=FALSE}
-post_sent_pos <- data.frame("Candidate" = c("Biden", "Sanders", "Warren", "Harris", "Buttigieg"), 
-                       "Positive" =c((sum(sentiments_jb_post$PositivityGI))/27477,
-                                      (sum(sentiments_bs_post$PositivityGI))/31603,                                                             (sum(sentiments_ew_post$PositivityGI))/18628,
-                                     (sum(sentiments_kh_post$PositivityGI))/16362,
-                                      (sum(sentiments_pb_post$PositivityGI))/27242))
-```
-
-### Google Trends
-This section describes gathering the Google Trends data using the package gtrends.
-First, we register our Google API key.
-Then, we pull data for each candidate from the 2 days preceding and two days following the debate (November 18 through 22).
-We have to pull the data in two separate blocks, because gtrends only allows us to use five search terms at a time.
-We limit the location of searches to the US.
-Please note that the key here is not a real API key, for security purposes.
-
-```{r, eval=FALSE, tidy=TRUE}
-register_google(key = "XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX")
-res1 <- gtrends(c("Joe Biden", "Bernie Sanders", 
-                  "Elizabeth Warren", "Kamala Harris", 
-                  "Pete Buttigieg"), geo = "US", 
-                time = "2019-11-18 2019-11-22", low_search_volume = T)
-
-res2 <- gtrends(c("Tom Steyer", "Andrew Yang", "Cory Booker", 
-                  "Amy Klobuchar", "Tulsi Gabbard"), geo = "US", 
-                time = "2019-11-18 2019-11-22", low_search_volume = T)
-```
-
-#### Geocoding
-
-Next, we compile and clean the Google Trends location data and prepare it for geocoding.
-
-```{r, , eval=FALSE}
-interest_by_location1 <- as_tibble(res1$interest_by_dma)
-interest_by_location2 <- as_tibble(res2$interest_by_dma)
-interest_by_location <- rbind(interest_by_location1, interest_by_location2)
-
-locations_df <- as.data.frame(interest_by_location)
-locations_df$location <- as.character(locations_df$location)
-```
-
-Then, we geocode the Google trends data.
-```{r, eval=FALSE}
-gc_locations <- as_tibble(mutate_geocode(locations_df, location))
-```
-
-#### Data Cleaning
-
-Next, we categorize the Google Trends data into pre-debate and post-debate data, based on the date.
-```{r, eval=FALSE}
-interest_over_time1 <- as_tibble(res1$interest_over_time)
-interest_over_time2 <- as_tibble(res2$interest_over_time)
-interest_over_time <- rbind(interest_over_time1, interest_over_time2)
-
-interest_over_time_pre <-
-  interest_over_time %>%
-  filter(date < "2019-11-19") %>%
-  mutate(Pre_post="Pre-debate")
-
-interest_over_time_post <-
-  interest_over_time %>%
-  filter(date > "2019-11-20") %>%
-  mutate(Pre_post="Post-debate")
-
-interest_over_time_all <- rbind(interest_over_time_pre, interest_over_time_post)
-```
-
-### Polls
-
-Polling data was collected from RealClearPolitics, which aggregates weekly polls.
-We created a dataset using the RealClearPolitics average before and after the November 20 debate.
-Because the website changes often, and we only needed a small snapshot of the data, it was more efficient to clean the data in Excel and import to R than to use web scraping.
-
-```{r, tidy=TRUE}
-github_link <- "https://github.com/znpadgett/surv727_padgett_thiam/raw/master/Data/Project%20polling%20data.xlsx"
-temp_file <- tempfile(fileext = ".xlsx")
-req <- GET(github_link, 
-           write_disk(path = temp_file))
-polling_data <- readxl::read_excel(temp_file)
-```
-
-## Results
-
-This section presents the main results.
-
-### Data exploration
-
-The results section may have a data exploration part, but in general the structure here depends on the specific project.
-
-#### Twitter
-
-Create a function to tabulate the count and proportion of tweets by candidates.
-
-##### Create functions
-```{r, eval=FALSE}
-type_var  <- unlist(map(pre_debate, class))
-
-freq_tab <- function(x) {
-# make table with count and frequency
-tab <- cbind(Count = table(x, useNA = "ifany"),
-Prop = round(prop.table(table(x, useNA = "ifany")),
-2))
-# get the categories as variable and rearrenge
-tab <- as.data.frame(tab) %>%
-tbl_df() %>%
-mutate(Cat = row.names(tab)) %>%
-select(Cat, Count, Prop)
-}
-
-```
-
-```{r, eval=FALSE}
-props1 <- map(pre_debate[, type_var == "logical"], freq_tab)
-props2 <- map(post_debate[, type_var == "logical"], freq_tab)
-
-vars <- unlist(map(props1, nrow))
-
-props_tab1 <- reduce(props1, rbind)
-props_tab2 <- reduce(props2, rbind)
-
-```
-
-```{r, eval=FALSE}
-props_tab1 <- props_tab1 %>%
-mutate(Variable = rep(names(vars), vars),
-       Candidate = ifelse(Variable == "BS", "Sanders",
-                   ifelse(Variable == "KH", "Harris",
-                   ifelse(Variable == "JB", "Biden",
-                   ifelse(Variable == "EW", "Warren",
-                   ifelse(Variable == "PB", "Buttigieg",
-                   ifelse(Variable == "TS", "Steyer",         
-                   ifelse(Variable == "AY", "Yang", 
-                   ifelse(Variable == "BC", "Booker",
-                   ifelse(Variable == "AK", "Klobuchar",
-                   ifelse(Variable == "TG", "Gabbard", NA)))))))))))
-
-props_tab2 <- props_tab2 %>%
-mutate(Variable = rep(names(vars), vars), 
-        Candidate = ifelse(Variable == "BS", "Sanders",
-                   ifelse(Variable == "KH", "Harris",
-                   ifelse(Variable == "JB", "Biden",
-                   ifelse(Variable == "EW", "Warren",
-                   ifelse(Variable == "PB", "Buttigieg",
-                   ifelse(Variable == "TS", "Steyer",         
-                   ifelse(Variable == "AY", "Yang", 
-                   ifelse(Variable == "BC", "Booker",
-                   ifelse(Variable == "AK", "Klobuchar",
-                   ifelse(Variable == "TG", "Gabbard", NA)))))))))))
-```
-
-A visual of the proportion of tweets pre and post debate
-
-##### Graphing
-###### Pre-debate number of tweets
-
-```{r, include=FALSE}
-#USE THIS CHUNK TO BRING IN props_tab1 and props_tab2
-source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/props_tab1.RData?raw=true")
-source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/props_tab2.RData?raw=true")
-
-```
-
-```{r, fig.cap="Pre-debate Mentions in Tweets, by Candidate"}
-props_tab1 %>%
-  filter(Cat == "TRUE") %>%
-  ggplot() +
-  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
-    labs(x = "Democatric Party Canditates", 
-       y = "Number of Tweets", 
-       caption = "Source: Twiiter")
-
-```
-
-###### Post-debate number of tweets 
-```{r, fig.cap="Post-debate Mentions in Tweets, by Candidate"}
-props_tab2 %>%
-  filter(Cat == "TRUE") %>%
-  ggplot() +
-  geom_col(mapping = aes(x = reorder(Variable, -Count), y=Count, fill = Variable)) +
-    labs(x = "Democatric Party Canditates", 
-       y = "Number of Tweets", 
-       caption = "Source: Twiiter")
-
-```
-
-#### Google Trends
-
-To explore the Google Trends data, we examined the location and density of searches for each candidate.
-We created a map showing our results.
-Because it was difficult to see the results for each candidate overlaid on one map, we added a facet wrap to show each individual candidate.
-```{r, include=FALSE}
-#USE THIS CHUNK TO BRING IN gc_locations
-source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/gc_locations.RData?raw=true")
-```
-
-```{r, message=FALSE, warning=FALSE, results="hide", fig.show="hide"}
-#get map
-us <- c(left = -125, bottom = 25.75, right = -67, top = 49)
-us_map <- get_stamenmap(us, zoom = 5, maptype = "toner-lite")
-ggmap(us_map) 
-```
-
-```{r, message=FALSE, warning=FALSE, fig.height=10, fig.width=12, fig.cap="Map of Google Trends Hits, by Candidate"}
-#clean data for mapping
-trends_map <-
-  gc_locations %>%
-  group_by(keyword, location) %>%
-  mutate("Hits"=sum(hits), Candidate=keyword)
-
-#generate map
-ggmap(us_map) + 
-  geom_point(data = trends_map, aes(x = lon, y = lat, size=Hits, color=Candidate), 
-             alpha = 0.2) +
-  theme(axis.line=element_blank(),axis.text.x=element_blank(),
-          axis.text.y=element_blank(),axis.ticks=element_blank(),
-          axis.title.x=element_blank(),
-          axis.title.y=element_blank()) +
-  facet_wrap("Candidate", shrink=FALSE)
-```
-
-We also explored the number of hits pre- and post- debate for each candidate.
+## Candidate Search Popularity
 ```{r, include=FALSE}
@@
 
-```{r, tidy=TRUE, fig.cap="Pre- and Post-debate Google Trends Data, by Candidate"}
+```{r, message=FALSE, tidy=TRUE, fig.cap="Pre- and Post-debate Google Trends Data, by Candidate"}
 interest_over_time_all$Pre_post <- factor(interest_over_time_all$Pre_post, 
@@
 
-#### Polling Data
+## Polling Data
+- Data from RealClearPolitics, average polling results pre- and post-debate
+```{r, include=FALSE, tidy=TRUE}
+github_link <- "https://github.com/znpadgett/surv727_padgett_thiam/raw/master/Data/Project%20polling%20data.xlsx"
+temp_file <- tempfile(fileext = ".xlsx")
+req <- GET(github_link, 
+           write_disk(path = temp_file))
+polling_data <- readxl::read_excel(temp_file)
+```
 
-For the polling data, we looked at the pre- and post-debate polling numbers for each candidate.
-```{r, tidy=TRUE, fig.cap="Pre- and Post-debate Polling Data, by Candidate"}
+```{r, message=FALSE, tidy=TRUE, fig.cap="Pre- and Post-debate Polling Data, by Candidate"}
 polling_data$Pre_post <- factor(polling_data$Pre_post, levels = c("Pre-debate", "Post-debate"))
@@
 
-### Analysis
-
-We created a Shiny app that allows us to compare the polling, Google Trends, and Twitter sentiment data.
-
-First, we cleaned up and combined the three data sources for use in the Shiny app.
-
+## Results
 ```{r, include=FALSE}
@@
 
-```{r, tidy=TRUE, warning=FALSE, message=FALSE}
+```{r, include=FALSE, tidy=TRUE, warning=FALSE, message=FALSE}
 #clean data
@@
 
-Then, we created a shiny app, which can be viewed by running the following code:
-```{r, eval=FALSE, tidy=TRUE}
+```{r, echo=FALSE, tidy=TRUE, warning=FALSE, message=FALSE}
 # Define UI
@@
 
-```{r}
-# What happens here depends on the specific project
-```
-
-```{r}
-# What happens here depends on the specific project
-```
-
-## Discussion
-
-This section summarizes the results and may briefly outline advantages and limitations of the work presented.
-
-## References
+## Conclusion

### 2019-12-08 Paper/paper-draft-Padgett-Thiam.Rmd
Update paper-draft-Padgett-Thiam.Rmd

@@
 
-This section describes the data sources and the data gathering process.
+Using the rtweet package and the search_tweet function, we were able to gather sufficient tweets for our project and classified it as pre or post debate.
+The initial dataset contains a little over 1.3 million tweets which was rich enough to proceed with analysis.
+After removing irrelevant tweets such as tweets containing "Ukraine", we were left with 1.2 million tweets which we then divided in two groups :pre and post debate.
+The pre-debate dataset has 226,799 tweets and 998,780 tweets for the post-debate dataset.
+As expected, there was a lot more tweets after the debate than before.
+With Twitter having a location column, we wanted to focus our anylysis on certain regions/ states in the U.S., however the location column is an open text and not regulated.
+We then picked a few states to focus our analysis on.
 

### 2019-12-08 Paper/paper-draft-Padgett-Thiam.Rmd
update references, add map figure

--- 2019-12-07 Paper/paper-draft-Padgett-Thiam.Rmd
@@
     year: 2017
+- id: Gtrendscite   
+  title: "gtrendsR: Perform and Display Google Trends Queries"
+  author:
+  - family: Massicotte
+    given: P.
+  - family: Eddelbuettel
+    given: D.
+  issued:
+    year: 2019
+  note: R package version 1.4.4.9000
+  url: https://github.com/PMassicotte/gtrendsR
+- id: shinycite
+  title: "shiny: Web Application Framework for R"
+  author:
+  - family: Chang
+    given: W.
+  - family: Cheng 
+    given: J.
+  - family: Allaire
+    given: J.
+  - family: Xie
+    given: Y. 
+  - family: McPherson
+    given: J.
+  issued:
+    year: 2019
+  note: R package version 1.4.0
+  url: https://CRAN.R-project.org/package=shiny
+- id: mapcite
+  title: "ggmap: Spatial Visualization with ggplot2"
+  author:
+  - family: Kahle
+    given: D.
+  - family: Wickham
+    given: H.
+  container-title: The R Journal
+  volume: 5
+  issue: 1
+  page: 144-161
+  type: article-journal
+  issued:
+    year: 2013
+  url: https://journal.r-project.org/archive/2013-1/kahle-wickham.pdf
 ---
-
-TO DO:
-- write results, and discussion sections
-- create presentation
 
@@
 [@Beauchamp2017], and to predict the winners of three presidential elections in Latin America [@Gaurav2013].
-Beauchamp (2017) found that Twitter data may be useful in making state-level campaign strategy decisions.
-Additionally, a recent study used Google Trends and Twitter data to predict the 2016 U.S.
-election outcomes with only 1% error [@Kassraie2017].
+@Beauchamp2017 found that Twitter data may be useful in making state-level campaign strategy decisions.
+Additionally, @Kassraie2017 used Google Trends and Twitter data to predict the 2016 U.S.
+election outcomes with only 1% error.
 
@@
 ### Google Trends
-This section describes gathering the Google Trends data using the package gtrends.
+This section describes gathering the Google Trends data using the package gtrendsR [@Gtrendscite].
 First, we register our Google API key.
@@
 
-This section presents the main results.
-
 ### Data exploration
 
-The results section may have a data exploration part, but in general the structure here depends on the specific project.
+Because our project was exploratory in nature, we spent significant time exploring each data source.
 
@@
 To explore the Google Trends data, we examined the location and density of searches for each candidate.
-We created a map showing our results.
+We created a map showing our results [@mapcite].
 Because it was difficult to see the results for each candidate overlaid on one map, we added a facet wrap to show each individual candidate.
@@
 
-We created a Shiny app that allows us to compare the polling, Google Trends, and Twitter sentiment data.
+We created a Shiny app that allows us to compare the polling, Google Trends, and Twitter sentiment data [@shinycite].
 
@@
 
-```{r}
-# What happens here depends on the specific project
-```
-
-```{r}
-# What happens here depends on the specific project
-```
-
 ## Discussion

### 2019-12-08 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
edit map

@@
 library(httr)
+library(magick)
 ```
@@
 - Graphed the search popularity of each candidate pre- and post-debate
+
+## Google Trends Map
+
+```{r, echo=FALSE, message=FALSE}
+image_read("https://github.com/znpadgett/surv727_padgett_thiam/raw/master/Paper/gtrends_map.png")
+```
 

### 2019-12-08 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
bring map into presentation from github
Update SURV727_FinalPresentation_Padgett_Thiam.Rmd

@@
 
-- Bullet 1
-- Bullet 2
-- Bullet 3
+- Used Rweet package and searh_tweet function with selected keywords to gather tweets between November 20th and November 21st
+- Separated the 1.3 million tweets after removing irrelevant tweets in 2 groups: pre and post debate
+- Generated maps by number of tweets per candidate and ran sentiment analysis for 5 candidates
+
+### Number of Tweets 
+```{r, include=FALSE}
+#USE THIS CHUNK TO BRING IN props_tab1 and props_tab2
+source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/props_tab1.RData?raw=true")
+source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/props_tab2.RData?raw=true")
+```
+### Pre-debate number of tweets 
+```{r, fig.cap="Pre-debate Mentions in Tweets, by Candidate"}
+props_tab1 %>%
+  filter(Cat == "TRUE") %>%
+  ggplot() +
+  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
+    labs(x = "Democatric Party Canditates", 
+       y = "Number of Tweets", 
+       caption = "Source: Twiiter") 
+```
+
+### Post-debate number of tweets 
+```{r, fig.cap="Post-debate Mentions in Tweets, by Candidate"}
+props_tab2 %>%
+  filter(Cat == "TRUE") %>%
+  ggplot() +
+  geom_col(mapping = aes(x = reorder(Variable, -Count), y=Count, fill = Variable)) +
+    labs(x = "Democatric Party Canditates", 
+       y = "Number of Tweets", 
+       caption = "Source: Twiiter")
+
+```
 
@@
 ```{r, echo=FALSE, message=FALSE}
-image_read("https://github.com/znpadgett/surv727_padgett_thiam/raw/master/Paper/gtrends_map.png")
+image_read("https://github.com/znpadgett/surv727_padgett_thiam/raw/master/Presentation/gtrends_map.png")
 ```

### 2019-12-08 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
update intro

--- 2019-12-08 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
@@
 
-This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
+- Can Twitter data and Google trends data be used to supplement polling results, by providing real-time information to candidates while they wait for polling data to come in?
+- Exploratory analysis to see if pre- and post-debate polling data during the 2020 U.S. Democratic primary election aligns with these real-time sources
 

### 2019-12-08 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
Update SURV727_FinalPresentation_Padgett_Thiam.Rmd

--- 2019-12-08 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
@@
 
-- Bullet 1
-- Bullet 2
-- Bullet 3
+- Used Rweet package and searh_tweet function with selected keywords to gather tweets between November 20th and November 21st
+- Separated the 1.3 million tweets after removing irrelevant tweets in 2 groups: pre and post debate
+- Generated maps by number of tweets per candidate and ran sentiment analysis for 5 candidates
+
+```{r, include=FALSE}
+#USE THIS CHUNK TO BRING IN props_tab1 and props_tab2
+source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/props_tab1.RData?raw=true")
+source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/props_tab2.RData?raw=true")
+```
+
+## Pre-debate number of tweets 
+```{r, fig.cap="Pre-debate Mentions in Tweets, by Candidate"}
+props_tab1 %>%
+  filter(Cat == "TRUE") %>%
+  ggplot() +
+  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
+    labs(x = "Democatric Party Canditates", 
+       y = "Number of Tweets", 
+       caption = "Source: Twiiter") 
+```
+
+## Post-debate number of tweets 
+```{r, fig.cap="Post-debate Mentions in Tweets, by Candidate"}
+props_tab2 %>%
+  filter(Cat == "TRUE") %>%
+  ggplot() +
+  geom_col(mapping = aes(x = reorder(Variable, -Count), y=Count, fill = Variable)) +
+    labs(x = "Democatric Party Canditates", 
+       y = "Number of Tweets", 
+       caption = "Source: Twiiter")
+
+```
 

### 2019-12-08 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
Update SURV727_FinalPresentation_Padgett_Thiam.Rmd

@@
        y = "Number of Tweets", 
-       caption = "Source: Twiiter") 
+       caption = "Source: Twitter") 
 ```
@@
   ggplot() +
-  geom_col(mapping = aes(x = reorder(Variable, -Count), y=Count, fill = Variable)) +
+  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
     labs(x = "Democatric Party Canditates", 
        y = "Number of Tweets", 
-       caption = "Source: Twiiter")
+       title = "Post Debate candidates mentions in Tweets", 
+       caption = "Source: Twitter")
+
+```
+
+## Tweets location pre-debate 
+```{r, fig.cap="Pre-debate Mentions in Tweets, by Candidate & location"}
+
+  ggplot() +
+  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
+    labs(x = "Democatric Party Canditates", 
+       y = "Number of Tweets", 
+       title = "Post Debate candidates mentions in Tweets", 
+       caption = "Source: Twitter")
+
+```
+
+## Tweets location post-debate 
+```{r, fig.cap="Post-debate Mentions in Tweets, by Candidate & location"}
+
+  ggplot() +
+  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
+    labs(x = "Democatric Party Canditates", 
+       y = "Number of Tweets", 
+       title = "Post Debate candidates mentions in Tweets", 
+       caption = "Source: Twitter")
 

### 2019-12-08 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
conclusion

--- 2019-12-08 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
@@
   geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
-    labs(x = "Democatric Party Canditates", 
+    labs(x = "Democratic Party Candidates", 
        y = "Number of Tweets", 
-       caption = "Source: Twiiter") 
+       caption = "Source: Twitter") 
 ```
@@
   ggplot() +
-  geom_col(mapping = aes(x = reorder(Variable, -Count), y=Count, fill = Variable)) +
-    labs(x = "Democatric Party Canditates", 
+  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
+    labs(x = "Democratic Party Candidates", 
        y = "Number of Tweets", 
-       caption = "Source: Twiiter")
+       title = "Post Debate candidates mentions in Tweets", 
+       caption = "Source: Twitter")
+
+```
+
+## Tweets location pre-debate 
+```{r, fig.cap="Pre-debate Mentions in Tweets, by Candidate & location"}
+
+  ggplot() +
+  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
+    labs(x = "Democratic Party Candidates", 
+       y = "Number of Tweets", 
+       title = "Post Debate candidates mentions in Tweets", 
+       caption = "Source: Twitter")
+
+```
+
+## Tweets location post-debate 
+```{r, fig.cap="Post-debate Mentions in Tweets, by Candidate & location"}
+
+  ggplot() +
+  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
+    labs(x = "Democratic Party Candidates", 
+       y = "Number of Tweets", 
+       title = "Post Debate candidates mentions in Tweets", 
+       caption = "Source: Twitter")
 
@@
 ## Conclusion
+
+- Neither Twitter nor Google Trends data align with polling data
+- These data are not representative of US voters, lack of demographic data for adjustment
+- Variable-to-variable comparison between two data sources may not be realistic (e.g., do number of searches and positivity of tweets actually mean more people will vote for a candidate?)
+- Many difficulties in practical usage of this data (e.g., location fields)
+- Overall, we don't think this data should be used in place of survey data
+- However, this data could still be useful for candidates in understanding how social media users percieve them before and after a debate, or in understanding their search popularity

### 2019-12-08 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
block location figures from running

@@
 ## Tweets location pre-debate 
-```{r, fig.cap="Pre-debate Mentions in Tweets, by Candidate & location"}
+```{r, eval=FALSE, fig.cap="Pre-debate Mentions in Tweets, by Candidate & location"}
 
@@
 ## Tweets location post-debate 
-```{r, fig.cap="Post-debate Mentions in Tweets, by Candidate & location"}
+```{r, eval=FALSE, fig.cap="Post-debate Mentions in Tweets, by Candidate & location"}
 

### 2019-12-08 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
Update SURV727_FinalPresentation_Padgett_Thiam.Rmd

--- 2019-12-08 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
@@
 
+ loc_pre_all %>%
+  mutate(Location = loc) %>%
+  group_by(Candidate, Location) %>%
+  summarise(total = n()) %>%
   ggplot() +
-  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
-    labs(x = "Democratic Party Candidates", 
+  geom_col(mapping = aes(x = reorder(Candidate, -total), y=total, fill = Location)) +
+    labs(x = "Democatric Party Canditates", 
        y = "Number of Tweets", 
-       title = "Post Debate candidates mentions in Tweets", 
-       caption = "Source: Twitter")
+       title = "Pre Debate candidates mentions in Tweets by location", 
+       caption = "Source: Twiiter")
 
@@
 
+ loc_post_all %>%
+  mutate(Location = loc) %>%
+  group_by(Candidate, Location) %>%
+  summarise(total = n()) %>%
   ggplot() +
-  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
-    labs(x = "Democratic Party Candidates", 
+  geom_col(mapping = aes(x = reorder(Candidate, -total), y=total, fill = Location)) +
+    labs(x = "Democatric Party Canditates", 
        y = "Number of Tweets", 
-       title = "Post Debate candidates mentions in Tweets", 
-       caption = "Source: Twitter")
+       title = "Post Debate candidates mentions in Tweets by location", 
+       caption = "Source: Twiiter")
 

### 2019-12-09 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
add tweet location data to pres

@@
 ```{r, include=FALSE}
-#USE THIS CHUNK TO BRING IN props_tab1 and props_tab2
+#USE THIS CHUNK TO BRING IN props_tab1 and props_tab2, loc_pre_all, and loc_post_all
 source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/props_tab1.RData?raw=true")
 source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/props_tab2.RData?raw=true")
+source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/loc_pre_all.RData?raw=true")
+source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/loc_post_all.RData?raw=true")
 ```

### 2019-12-09 Paper/paper-draft-Padgett-Thiam.Rmd
Update paper-draft-Padgett-Thiam.Rmd

@@
 ## References
+
+ Kearney, M. W. (2018). rtweet: Collecting Twitter Data. R package version 0.6.7 
+ Retrieved from https://cran.r-project.org/package=rtweet
+
+ Silge J, Robinson D (2016). “tidytext: Text Mining and Analysis Using Tidy Data Principles in R.” _JOSS_, *1*(3). 
+ doi: 10.21105/joss.00037 (URL http://doi.org/10.21105/joss.00037), <URL:http://dx.doi.org/10.21105/joss.00037>.
+
+ D. Kahle and H. Wickham. ggmap: Spatial Visualization with ggplot2.
+ The R Journal, 5(1), 144-161. URL http://journal.r-project.org/archive/2013-1/kahle-wickham.pdf
+
+ Garrett Grolemund, Hadley Wickham (2011). Dates and Times Made Easy with
+ lubridate. Journal of Statistical Software, 40(3), 1-25. URL http://www.jstatsoft.org/v40/i03/.
+
+ Benoit K, Watanabe K, Wang H, Nulty P, Obeng A, Müller S, Matsuo A (2018).  “quanteda: An R package for the quantitative
+ analysis of textual data.” _Journal of Open Source Software_, *3*(30), 774. doi: 10.21105/joss.00774 
+ (URL: http://doi.org/10.21105/joss.00774), <URL: https://quanteda.io>.
+
+  Stefan Feuerriegel and Nicolas Proellochs (2019). SentimentAnalysis: Dictionary-Based Sentiment Analysis. 
+  R package version 1.3-3. https://CRAN.R-project.org/package=SentimentAnalysis
+
+  Barret Schloerke, Jason Crowley, Di Cook, Francois Briatte, Moritz Marbach, Edwin Thoen, 
+  Amos Elberg and Joseph Larmarange (2018). GGally:  Extension to 'ggplot2'. R package version 1.4.0. 
+  https://CRAN.R-project.org/package=GGally
+
+   H. Wickham. ggplot2: Elegant Graphics for Data Analysis. Springer-Verlag New York, 2016.
+
+  Gergely Daróczi and Roman Tsegelskyi (2018). pander: An R 'Pandoc'  Writer. R package version 0.6.3.
+  https://CRAN.R-project.org/package=pander

### 2019-12-09 Paper/paper-draft-Padgett-Thiam.Rmd
Update paper-draft-Padgett-Thiam.Rmd

@@
 As expected, there was a lot more tweets after the debate than before.
-With Twitter having a location column, we wanted to focus our anylysis on certain regions/ states in the U.S., however the location column is an open text and not regulated.
-We then picked a few states to focus our analysis on.
+Twitter has a location field since we wanted to focus our anylysis on certain states in the U.S., however the location column is an open text and not regulated.
+We selected severals states: New York, Virginia, New Hampshire, Nevada, Illinois, Iowa, Ohio, California and DC to focus our analysis on.
 
@@
 source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/props_tab2.RData?raw=true")
+source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/loc_pre_all.RData?raw=true")
+source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/loc_post_all.RData?raw=true")
 
 ```
-
+## Pre-debate number of tweets 
 ```{r, fig.cap="Pre-debate Mentions in Tweets, by Candidate"}
@@
   geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
-    labs(x = "Democatric Party Canditates", 
+    labs(x = "Democratic Party Candidates", 
        y = "Number of Tweets", 
-       caption = "Source: Twiiter")
+           caption = "Source: Twitter
+
+                                 Figure 1") +
+theme(axis.text.x=element_text(angle=90,hjust=1))
 
 ```
+Figure 1 shows the number of tweets that mentioned each candidate before the debate. We noticed that Sanders, Biden and Buttigieg are in the lead with a little over 25,000 mentions.
 
-###### Post-debate number of tweets 
+## Post-debate number of tweets 
 ```{r, fig.cap="Post-debate Mentions in Tweets, by Candidate"}
@@
   ggplot() +
-  geom_col(mapping = aes(x = reorder(Variable, -Count), y=Count, fill = Variable)) +
-    labs(x = "Democatric Party Canditates", 
+  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
+    labs(x = "Democratic Party Candidates", 
        y = "Number of Tweets", 
-       caption = "Source: Twiiter")
+       title = "Post Debate candidates mentions in Tweets", 
+            caption = "Source: Twitter
+
+                                 Figure 2") +
+theme(axis.text.x=element_text(angle=90,hjust=1))
+
+```
+
+Figure 2 shows the post- debate tweets mentions by candidate.
+As expected lots more tweets mentions occured after the debate, 5 times more than pre- debate.
+Here we noticed that the ranking change with Harris and Yang in the lead along with Sanders.
+
+## Tweets location pre-debate 
+```{r, fig.cap="Pre-debate Mentions in Tweets, by Candidate & location"}
+
+ loc_pre_all %>%
+  mutate(Location = loc) %>%
+  group_by(Candidate, Location) %>%
+  summarise(total = n()) %>%
+  ggplot() +
+  geom_col(mapping = aes(x = reorder(Candidate, -total), y=total, fill = Location)) +
+    labs(x = "Democratic Party Canditates", 
+       y = "Number of Tweets", 
+       title = "Pre Debate candidates mentions in Tweets by location", 
+             caption = "Source: Twitter
+
+                                 Figure 3") +
+           theme(axis.text.x=element_text(angle=90,hjust=1))
+
+```
+Figure 3 .....
+## Tweets location post-debate 
+```{r, fig.cap="Post-debate Mentions in Tweets, by Candidate & location"}
+
+ loc_post_all %>%
+  mutate(Location = loc) %>%
+  group_by(Candidate, Location) %>%
+  summarise(total = n()) %>%
+  ggplot() +
+  geom_col(mapping = aes(x = reorder(Candidate, -total), y=total, fill = Location)) +
+    labs(x = "Democratic Party Canditates", 
+       y = "Number of Tweets", 
+       title = "Post Debate candidates mentions in Tweets by location", 
+              caption = "Source: Twitter
+
+                                 Figure 4") +
+theme(axis.text.x=element_text(angle=90,hjust=1))
 

### 2019-12-09 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
Update SURV727_FinalPresentation_Padgett_Thiam.Rmd

@@
        y = "Number of Tweets", 
-       caption = "Source: Twitter") 
+           caption = "Source: Twitter
+
+                                 Figure 1") +
+theme(axis.text.x=element_text(angle=90,hjust=1))
+
 ```
@@
        title = "Post Debate candidates mentions in Tweets", 
-       caption = "Source: Twitter")
+            caption = "Source: Twitter
+
+                                 Figure 2") +
+theme(axis.text.x=element_text(angle=90,hjust=1))
 
@@
        title = "Pre Debate candidates mentions in Tweets by location", 
-       caption = "Source: Twiiter")
+             caption = "Source: Twitter
+
+                                 Figure 3") +
+           theme(axis.text.x=element_text(angle=90,hjust=1))
 
@@
        title = "Post Debate candidates mentions in Tweets by location", 
-       caption = "Source: Twiiter")
+              caption = "Source: Twitter
+
+                                 Figure 4") +
+theme(axis.text.x=element_text(angle=90,hjust=1))
 

### 2019-12-10 Paper/paper-draft-Padgett-Thiam.Rmd
Update paper-draft-Padgett-Thiam.Rmd

@@
   url: https://journal.r-project.org/archive/2013-1/kahle-wickham.pdf
+- id: Gtrendscite   
+  title: "gtrendsR: Perform and Display Google Trends Queries"
+  author:
+  - family: Massicotte
+    given: P.
+  - family: Eddelbuettel
+    given: D.
+  issued:
+    year: 2019
+  note: R package version 1.4.4.9000
+  url: https://github.com/PMassicotte/gtrendsR
+- id: rtweet
+  title: "rtweet: Collecting Twitter Data"
+  author:
+  - family: Kearney
+    given: M.
+  issued:
+    year: 2019
+  note: R package version 0.6.9
+  url: https://cran.r-project.org/package=rtweet
+- id: tidytext
+  title: "tidytext: Text Mining and Analysis Using Tidy Data Principles in R"
+  author:
+  - family: Silge
+    given: J.
+  - family: Robinson
+    given: D.
+  doi: 10.21105/joss.00037
+  url: http://dx.doi.org/10.21105/joss.00037
+  issued:
+    year: 2016
+  publisher: The Open Journal
+  note: R package version 0.6.9
+  volume: 1
+  number: 3
+  journal: JOSS
+- id: sentiment
+  title: "SentimentAnalysis: Dictionary-Based Sentiment Analysis"
+  author:
+  - family: Feuerriegel
+    given: S.
+  - family: Proellochs
+    given: N.
+  doi: 10.21105/joss.00037
+  url: https://CRAN.R-project.org/package=SentimentAnalysis
+  issued:
+    year: 2019
+  note: R package version 1.3-3
+- id: quanteda
+  title: "quanteda: An R package for the quantitative analysis of textual data"
+  author:
+  - family: Benoit
+    given: K.
+  - family: Watanabe
+    given: K.
+  - family: Wang
+    given: H.
+  - family: Nulty
+    given: P.
+  - family: Obeng
+    given: A.
+  - family: Müller
+    given: S.
+  - family: Matsuo
+    given: A.
+  doi: 10.21105/joss.00774
+  url: https://quanteda.io
+  issued:
+    year: 2018
+  volume: 3
+    number: 30
+    pages: 774
+- id: tidyverse
+  title: "tidyverse: Easily Install and Load the 'Tidyverse'"
+  author:
+  - family: Wickman
+    given: H.
+  url: https://CRAN.R-project.org/package=tidyverse
+  issued:
+    year: 2017
+  note: R package version 1.2.1
+
 ---
@@
 
-Using the rtweet package and the search_tweet function, we were able to gather sufficient tweets for our project and classified it as pre or post debate.
+Using the rtweet package and the search_tweet function, we were able to gather sufficient tweets for our project and seperated in two datasets; pre- and post- debate.
 The initial dataset contains a little over 1.3 million tweets which was rich enough to proceed with analysis.
-After removing irrelevant tweets such as tweets containing "Ukraine", we were left with 1.2 million tweets which we then divided in two groups :pre and post debate.
+After removing irrelevant tweets such as tweets containing "Ukraine", we were left with over 1.2 million tweets.
+This was used to create the pre- and post- debate datasets.
 The pre-debate dataset has 226,799 tweets and 998,780 tweets for the post-debate dataset.
 As expected, there was a lot more tweets after the debate than before.
-Twitter has a location field since we wanted to focus our anylysis on certain states in the U.S., however the location column is an open text and not regulated.
-We selected severals states: New York, Virginia, New Hampshire, Nevada, Illinois, Iowa, Ohio, California and DC to focus our analysis on.
+We used the  Twitter location field to perform analysis at the state level.However, the location column is an open text and not regulated.
+We selected severals states such New York, Virginia, New Hampshire, Nevada, Illinois, Iowa, Ohio, California and DC to focus our analysis on.
 
@@
 
-Using the search_tweets function in the rtweets package, we will be quering tweets with the keywords specified below.
-We limited our tweets pool to November 20th and November 21st.
-The reasonning behind this is to get a feel post and pre debate.
+Using the search_tweet function in the rtweet package, we will be quering tweets with the specified keywords below.
+We limited our tweets pull to November 20th and November 21st.
+The reasonning behind this is to get a sense on how Twitter users feel pre- and post- debate.
 
@@
 
-Even after we specify the keywords, we know that we would still get irrelevants tweets mainly with the Ukraine issue at the time of pulling. We removed all tweets that had the word "Ukraine" in it.
+Even with specified keywords, irrelevants tweets were also made it to the initial dataset mainly with the Ukraine issue at the time of pulling.
+We removed all tweets that had the word "Ukraine" in order to focus completly on tweets regarding the debate.
 
 ```{r, eval=FALSE}
-myvars <- c("text", "location", "created_at")
-df1 <- dem[myvars]
-df2 <- dem2[myvars]
+vars <- c("text", "location", "created_at")
+df1 <- dem[vars]
+df2 <- dem2[vars]
 ```
@@
 
-Next, we seperate the tweets by candidates in order to do the analysis at the candidate level.
+Next, we seperate the tweets by candidates in order to do analysis at the candidate level.
 It's important to note that one tweets can be addressed to multiple candidates.
-In that case, the tweet will be found in the each of those candidate dataset.
+In that case, the tweet will be found in the each of those candidates dataset.
 The code below exemplifies this step of the cleaning process.
@@
 
-Here we reformat the created_at column as a date & time variable in order to seperate the tweets in two groups : post and pre debate.
+Here we reformat the created_at column as a date & time variable in order to seperate the tweets in two groups : pre- and post- debate.
 ```{r, eval=FALSE}
@@
 All the tweets received before 9 p.m.
-on November 20th are accounted for in the pre-debate dataset and all tweets from 11 p.m.
+on November 20th were accounted for in the pre-debate dataset and all tweets from 11 p.m.
 on November 20th to the next day are in the post-debate dataset.
-Note that tweets during the debate( 9 - 11 p.m are ignored)
+Note that tweets during the debate( 9 - 11 p.m.
+were removed)
 ```{r, eval=FALSE, tidy=TRUE}
@@
 #### Sentiment Analysis
-Sentiment analysis of the tweets will performed for only 5 candidates.
+Sentiment analysis of the tweets will not be performed for all candidates but only 5 : Harris, Sanders, Biden, Warren & Buttigieg.
 
 First we need to prep the tweets by removing all non-words such as emojis and use the sentiment analysis package for analysis.
-Althought the sentiment analysis packae uses 5 dictionnairies, we will only look at the results from the GI dictionnary.
-For the pre-debate tweets sentimeent we used all the tweets from the dataset; however for the post-debate analysis, we sampled from the dataset due to volume and processing error.
+Althought the sentiment analysis package uses 5 dictionnairies, we will only look at the results from the GI dictionnary.
+For the pre-debate tweets sentiment analysis, we used all the tweets from the dataset.
+However, for the post-debate sentiment analysis we sampled from the dataset due to volume and space issue.
 The code below exemplifies this process.
+The sample size for each candidate post-debate dataset is the same as the pre-debate number of tweets for consistency.
+For instance, the pre-debate dataset for Sanders had 31,603 tweets, the sample size for the post-debate dataset for Sanders was 31,603.
 ```{r, eval=FALSE}
@@
 
+Table 1 shows the number of mentions by candidate pre- and post- debate and Table 2 shows similar results adding location as a factor.
+In both tables, we see that there were lot more tweets after the debate.
+This was anticipated with the debate being a headline the next day.
+This was also the reason why we decided to focus on pre- and post- debate analysis and not focus on the number of tweets.
+Sentiment analysis was performed using the GI dictionnaire in the sentiment analysis package [@sentiment].Each tweet received a positive, neutral and/ or negative score.
+For this project, we summed the positive score of all tweets and divided by the number of tweets in each dataset.
+This gave us the average tweet positivity by candidate shown in Table 3.
+Candidate tweet positivity pre- debate are very close with xx% for candx being the highest.
+We notice a slight increase for almost all candidates with now xx% forcandx in the lead.
+
 ### Data exploration
@@
 ```
-Figure 1 shows the number of tweets that mentioned each candidate before the debate. We noticed that Sanders, Biden and Buttigieg are in the lead with a little over 25,000 mentions.
+Figure 1 shows the number of tweets that mentioned each candidate before the debate. We noticed that Sanders, Biden and Buttigieg are in the lead with over 25,000 tweets mentions.
 
@@
 Figure 2 shows the post- debate tweets mentions by candidate.
-As expected lots more tweets mentions occured after the debate, 5 times more than pre- debate.
-Here we noticed that the ranking change with Harris and Yang in the lead along with Sanders.
+As expected, lot more tweets mentions occured after the debate, about 5 times more than pre- debate.
+Here we noticed that the ranking change with Harris and Yang in the lead along with Sanders and tweets mentions close to 150,000.
 
@@
 ```
-Figure 3 .....
+Figure 3 shows the number of tweets mentions by candidate by location pre- debate.
+Here we notice that Buttigieg, Sanders and Yang get the most tweets mentions and mainly coming from California and New York for all 3 candidates.
+These results are not surprising with California and New York population presence in Twitter.
+
 ## Tweets location post-debate 
@@
 ```
+Figure 4 is the post- debate tweets mentions by candidate by location.
+Just like in Figure 3 (pre-debate analysis) California and New York had the most users tweeting about the candidates.Harris, Yang and Sanders are mostly mentionned in tweets by users.
 
@@
 
-This section summarizes the results and may briefly outline advantages and limitations of the work presented.
+It would be advantageous to survey methodologists to be able to use sources such as Twitter to replace survey data.
+However, we need to aknowledge the limitations preventing us from doing so.
+We all will agree that Twitter users do not adequately represent the population consequently introducing coverage error.
+Validity and measurement error just to name a few limitations we encountered with Twitter data.
+In lieu of replacing survey data, Twitter data can/ should be use as a supplemental data.
+It is important to note that we collected data for a short period of time.
+We believed that Twitter data can be much more useful if we had a longer timeframe.
+With that we would be able to perform more in depht analysis with time a key variable or even fit models.
+For instance, the next democratic debate is scheduled for December 19th, it would be intersting to see how the sentiment differ from the November 21st debate.
+On that point, candidates could use Twitter data for many other purposes such as percpetion in the Twitter world or change over time in sentiment but definitely not for election outcomes.
 
 ## References
-
- Kearney, M. W. (2018). rtweet: Collecting Twitter Data. R package version 0.6.7 
- Retrieved from https://cran.r-project.org/package=rtweet
-
- Silge J, Robinson D (2016). “tidytext: Text Mining and Analysis Using Tidy Data Principles in R.” _JOSS_, *1*(3). 
- doi: 10.21105/joss.00037 (URL http://doi.org/10.21105/joss.00037), <URL:http://dx.doi.org/10.21105/joss.00037>.
-
- D. Kahle and H. Wickham. ggmap: Spatial Visualization with ggplot2.
- The R Journal, 5(1), 144-161. URL http://journal.r-project.org/archive/2013-1/kahle-wickham.pdf
-
- Garrett Grolemund, Hadley Wickham (2011). Dates and Times Made Easy with
- lubridate. Journal of Statistical Software, 40(3), 1-25. URL http://www.jstatsoft.org/v40/i03/.
-
- Benoit K, Watanabe K, Wang H, Nulty P, Obeng A, Müller S, Matsuo A (2018).  “quanteda: An R package for the quantitative
- analysis of textual data.” _Journal of Open Source Software_, *3*(30), 774. doi: 10.21105/joss.00774 
- (URL: http://doi.org/10.21105/joss.00774), <URL: https://quanteda.io>.
-
-  Stefan Feuerriegel and Nicolas Proellochs (2019). SentimentAnalysis: Dictionary-Based Sentiment Analysis. 
-  R package version 1.3-3. https://CRAN.R-project.org/package=SentimentAnalysis
-
-  Barret Schloerke, Jason Crowley, Di Cook, Francois Briatte, Moritz Marbach, Edwin Thoen, 
-  Amos Elberg and Joseph Larmarange (2018). GGally:  Extension to 'ggplot2'. R package version 1.4.0. 
-  https://CRAN.R-project.org/package=GGally
-
-   H. Wickham. ggplot2: Elegant Graphics for Data Analysis. Springer-Verlag New York, 2016.
-
-  Gergely Daróczi and Roman Tsegelskyi (2018). pander: An R 'Pandoc'  Writer. R package version 0.6.3.
-  https://CRAN.R-project.org/package=pander

### 2019-12-11 Paper/paper-draft-Padgett-Thiam.Rmd
fix paper issues

@@
   pdf_document:
+    fig_caption: yes        
+    includes:  
+      in_header: fix_float.tex
     toc: yes
@@
 ```
-
+\newpage
 ## Introduction
@@
 on November 20th to the next day are in the post-debate dataset.
-Note that tweets during the debate( 9 - 11 p.m.
-were removed)
+Note that tweets during the debate (9 - 11 p.m.) were removed.
 ```{r, eval=FALSE, tidy=TRUE}
@@
 Then, we pull data for each candidate from the 2 days preceding and two days following the debate (November 18 through 22).
-We have to pull the data in two separate blocks, because gtrends only allows us to use five search terms at a time.
+We have to pull the data in two separate blocks, because gtrendsR only allows us to use five search terms at a time.
 We limit the location of searches to the US.
@@
 
-Polling data was collected from RealClearPolitics, which aggregates weekly polls.
+Polling data was collected from RealClearPolitics.com, which aggregates weekly polls.
 We created a dataset using the RealClearPolitics average before and after the November 20 debate.
@@
 ```
-## Pre-debate number of tweets 
+
+###### Pre-debate number of tweets
+
 ```{r, fig.cap="Pre-debate Mentions in Tweets, by Candidate"}
@@
 
-## Post-debate number of tweets 
+###### Post-debate number of tweets 
 ```{r, fig.cap="Post-debate Mentions in Tweets, by Candidate"}
@@
 theme(axis.text.x=element_text(angle=90,hjust=1)) 
-
-```
-
+```
+
+\newpage
 Figure 2 shows the post- debate tweets mentions by candidate.
@@
 
-## Tweets location pre-debate 
+###### Tweets location pre-debate 
 ```{r, fig.cap="Pre-debate Mentions in Tweets, by Candidate & location"}
@@
 
-## Tweets location post-debate 
+###### Tweets location post-debate 
 ```{r, fig.cap="Post-debate Mentions in Tweets, by Candidate & location"}
@@
 theme(axis.text.x=element_text(angle=90,hjust=1)) 
-
 ```
@@
 ```
+
+These maps show that candidates have different distributions and density of searches. Searches are more common near the coasts, and less common in the middle of the country.
 
@@
 ```
+
+All candidates had higher search counts after the debate than before.
+This makes sense, because after a debate there is an increase in the number of news stories about candidates, which may lead to increased interest and thus, increased search activity.
+Additionally, users may be searching Google to learn about a candidate's debate performance if they did not watch the debate live.
 
@@
 
+When looking at the pre- and post-debate data from each source side-by-side, we can see that, while candidates who are polling higher have higher numbers of tweets and Google searches (for the most part), there is no clear relationship between the post-debate changes in polling numbers and the post-debate changes in Twitter and Google Trends data.
+Regardless of polling numbers, all candidates had higher Twitter positivity ratings and higher numbers of Google searches post-debate than pre-debate.
+
 ## Discussion
+
+Our results show that neither Twitter nor Google Trends data align with pre- and post-debate changes in polling numbers There were no discernable patterns that relate the found data to the polling data.
+There may be many reasons why the found data did not align with the polling data.
+For one, the found data are not representative of U.S.
+voters, only Twitter users or Google searches, and the lack of availability of demographic data does not allow for weighting adjustments.
+Variable-to-variable comparison between two data sources may not be realistic.
+For example, a large number of searches and higher positivity of tweets may not actually mean that more people will vote for a candidate.
+
+Additionally, there are many practical difficulties in using the found data, for example that the location field in the Twitter data corresponds to self-reported location, an open-ended field.
+Many users give incorrect or fake locations.
+
+Overall, we don't think that this data should be used in place of survey data when it comes to election polling.
+However, this data could still be useful for candidates in understanding how social media users percieve them before and after a debate, or in understanding their search popularity.
+It is important to recognize that these measures are not an accurate proxy for voter opinion, but they could still be useful in their own right.
+Campaigns would also need to recognize that the target population of any inferences may on these data is not U.S.
+voters, or even all those living in the U.S., but is actually the population of tweets (for the Twitter data) or Google searches (for the Google Trends data).
+When these considerations are taken into account, we still think that this data could be useful for campaign strategy.
 

### 2019-12-11 Paper/paper-draft-Padgett-Thiam.Rmd
re-knit paper

@@
     given: D.
-  doi: 10.21105/joss.00037
-  url: http://dx.doi.org/10.21105/joss.00037
+  url: "http://dx.doi.org/10.21105/joss.00037"
   issued:
@@
     given: N.
-  doi: 10.21105/joss.00037
   url: https://CRAN.R-project.org/package=SentimentAnalysis
@@
     given: A.
-  doi: 10.21105/joss.00774
   url: https://quanteda.io
@@
     year: 2018
-  volume: 3
-    number: 30
-    pages: 774
 - id: tidyverse
@@
   note: R package version 1.2.1
-
 ---
@@
 tweets <- rbind(df1, df2)
-
 ```
@@
 df1$TG <-(str_detect(df1$text, regex("#gabbard |@TulsiGabbard", ignore_case = TRUE)))
-
 ```
@@
 df2$TG <-(str_detect(df2$text, regex("#gabbard |@TulsiGabbard", ignore_case = TRUE)))
-
 ```

### 2019-12-11 Paper/paper-draft-Padgett-Thiam.Rmd
additional graphs

@@
 library(httr)
+library(rsconnect)
 ```
@@
   mutate(Candidate=keyword, Data="GTrends") %>%
+  filter(Candidate %in% c("Joe Biden", "Bernie Sanders", 
+                          "Elizabeth Warren", "Kamala Harris", 
+                          "Pete Buttigieg")) %>%
   group_by(Candidate, Pre_post, Data) %>%
+  arrange(Candidate, Pre_post) %>%
   summarise(Percentage=mean(hits))
@@
   select(Candidate, Pre_post, Percentage) %>%
+  filter(Candidate %in% c("Joe Biden", "Bernie Sanders", 
+                          "Elizabeth Warren", "Kamala Harris", 
+                          "Pete Buttigieg")) %>%
   mutate(Data="Polling") %>%
+  arrange(Candidate, Pre_post) %>%
   group_by(Candidate, Pre_post, Data)
@@
   group_by(Candidate, Pre_post, Data) %>%
+  arrange(Candidate, desc(Pre_post)) %>%
   mutate(Percentage=Percentage*100)
@@
 
-Then, we created a shiny app, which can be viewed by running the following code:
+Then, we created a shiny app, which can be viewed at https://znpadgett.shinyapps.io/shinyapp/:
 ```{r, eval=FALSE, tidy=TRUE}
 # Define UI
+surv727app <-
 ui <- fluidPage(
@@
 shinyApp(ui = ui, server = server)
-
-```
-
+```
+
+```{r, eval=FALSE, include=FALSE}
+#upload shiny app to the web - fake secret
+rsconnect::setAccountInfo(name='znpadgett',
+			  token='DA192A4A3FA4FB169FE8B04D20CA9CEA',
+			  secret='XXXXXXXXXXXXXXXXXXXXXXXXXX')
+```
+
+Finally, we examined the relationships between the polling data and the Twitter and Google Trends data post-debate, as well as the relationships between pre- and post-debate changes across data sources.
+
+```{r, tidy=TRUE, fig.cap="Comparison of Post-debate Twitter and Polling Data"}
+graphing_data <- cbind(twitter, poll, gtrends)
+graphing_data %>%
+  group_by(Pre_post, Candidate) %>%
+  filter(Pre_post=="Post-debate") %>%
+  ggplot() +
+  geom_point(mapping = aes(x=Percentage, y=Percentage1, color=Candidate), size=4) +
+  xlim(0,20) +
+  ylim(0,30) +
+  labs(x="Twitter Sentiment", 
+       y="Polling Data")
+```
+
+```{r, tidy=TRUE, fig.cap="Comparison of Post-debate Google Trends and Polling Data"}
+graphing_data  %>%
+  group_by(Pre_post, Candidate) %>%
+  filter(Pre_post=="Post-debate") %>%
+  ggplot() +
+  geom_point(mapping = aes(x=Percentage2, y=Percentage1, color=Candidate), size=4) +
+  xlim(0,100) +
+  ylim(0,30) +
+  labs(x="Google Trends Data", 
+       y="Polling Data")
+```
+
+```{r, tidy=TRUE, fig.cap="Comparison of Changes in Twitter and Polling Data"}
+print(graphing_data)
+pre <-
+graphing_data  %>%
+  select(Pre_post, Candidate, Percentage, Percentage1, Percentage2) %>%
+  group_by(Pre_post, Candidate) %>%
+  filter(Pre_post=="Pre-debate") %>%
+  mutate(Pre_twitter=Percentage, Pre_polling=Percentage1, Pre_gtrends=Percentage2)
+
+post <-
+  graphing_data  %>%
+  select(Pre_post, Candidate, Percentage, Percentage1, Percentage2) %>%
+  group_by(Pre_post, Candidate) %>%
+  filter(Pre_post=="Post-debate") %>%
+  mutate(Post_twitter=Percentage, Post_polling=Percentage1, Post_gtrends=Percentage2)
+
+change_data <- cbind(pre, post)
+
+change_data %>%
+  group_by(Pre_post, Candidate) %>%
+  mutate(change_twitter = ((Post_twitter - Pre_twitter) / Pre_twitter) * 100, 
+         change_polling = ((Post_polling - Pre_polling) / Pre_polling) * 100, 
+         change_gtrends = ((Post_gtrends - Pre_gtrends) / Pre_gtrends) * 100) %>%
+  ggplot() +
+  geom_point(mapping = aes(x=change_twitter, y=change_polling, color=Candidate), size=4) +
+  labs(x="Percent Change in Twitter Sentiment", 
+       y="Percent Change in Polling Data")
+
+```
+
+```{r, tidy=TRUE, fig.cap="Comparison of Changes in Google Trends and Polling Data"}
+change_data %>%
+  group_by(Pre_post, Candidate) %>%
+  mutate(change_twitter = ((Post_twitter - Pre_twitter) / Pre_twitter) * 100, 
+         change_polling = ((Post_polling - Pre_polling) / Pre_polling) * 100, 
+         change_gtrends = ((Post_gtrends - Pre_gtrends) / Pre_gtrends) * 100) %>%
+  ggplot() +
+  geom_point(mapping = aes(x=change_gtrends, y=change_polling, color=Candidate), size=4) +
+  labs(x="Percent Change in Google Trends Data", 
+       y="Percent Change in Polling Data")
+```
 When looking at the pre- and post-debate data from each source side-by-side, we can see that, while candidates who are polling higher have higher numbers of tweets and Google searches (for the most part), there is no clear relationship between the post-debate changes in polling numbers and the post-debate changes in Twitter and Google Trends data.
@@
 
-It would be advantageous to survey methodologists to be able to use sources such as Twitter to replace survey data.
-However, we need to aknowledge the limitations preventing us from doing so.
+It would be advantageous to survey methodologists to be able to use sources such as Twitter and Google Trends to replace survey data.
+However, we need to acknowledge the limitations preventing us from doing so.
 We all will agree that Twitter users do not adequately represent the population consequently introducing coverage error.
 Validity and measurement error just to name a few limitations we encountered with Twitter data.
-In lieu of replacing survey data, Twitter data can/ should be use as a supplemental data.
-It is important to note that we collected data for a short period of time.
+In lieu of replacing survey data, Twitter data can and should be use as a supplemental data.
+It is also important to note that we collected data for a short period of time.
 We believed that Twitter data can be much more useful if we had a longer timeframe.

### 2019-12-11 Paper/paper-draft-Padgett-Thiam.Rmd
Update paper-draft-Padgett-Thiam.Rmd

@@
 library(rsconnect)
+library(pander)
+
 ```
@@
 
-Table 1 shows the number of mentions by candidate pre- and post- debate and Table 2 shows similar results adding location as a factor.
+Table 1 shows the number of mentions by candidate pre- and post- debate and Table 2 (CA only) shows similar results adding location as a factor.
 In both tables, we see that there were lot more tweets after the debate.
@@
 This gave us the average tweet positivity by candidate shown in Table 3.
-Candidate tweet positivity pre- debate are very close with xx% for candx being the highest.
-We notice a slight increase for almost all candidates with now xx% forcandx in the lead.
+Candidate tweet positivity scrore pre- debate are very close with 15% for Sanders being the highest.
+We notice a slight increase for all candidates with Sanders in the lead still at 16%.
+
+```{r, include=FALSE}
+#USE THIS CHUNK TO BRING IN table1, table2 and table3
+source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/table1.RData?raw=true")
+source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/table2.RData?raw=true")
+source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/table3.RData?raw=true")
+```
+
+```{r}
+panderOptions('table.caption.prefix', 'Table 1: ')
+pander(table1 ,caption = "Count of tweets that mentionned candidates pre- and post- debate.")
+```
+
+```{r}
+panderOptions('table.caption.prefix', 'Table 2: ')
+pander(table2 ,caption = "Count of tweets that mentionned candidates in California pre- and post- debate.")
+```
+
+```{r}
+panderOptions('table.caption.prefix', 'Table 3: ')
+pander(table3 ,caption = "Sentiment Analysis average positivity score pre- and post- debate by candidate.")
+```
 
@@
 ```{r, include=FALSE}
-#USE THIS CHUNK TO BRING IN props_tab1 and props_tab2
+#USE THIS CHUNK TO BRING IN props_tab1, props_tab2, loc_pre_all and loc_post_all 
 source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/props_tab1.RData?raw=true")

### 2019-12-11 Paper/paper-draft-Padgett-Thiam.Rmd
put app online

@@
 library(httr)
-library(rsconnect)
 library(pander)
-
 ```
@@
                                                           "Post-debate"))
-```
-
-Then, we created a shiny app, which can be viewed at https://znpadgett.shinyapps.io/shinyapp/:
+
+```
+
+Then, we created a shiny app, which can be viewed at https://znpadgett.shinyapps.io/surv727app/:
 ```{r, eval=FALSE, tidy=TRUE}
 # Define UI
-surv727app <-
+
 ui <- fluidPage(
@@
 
-```{r, eval=FALSE, include=FALSE}
-#upload shiny app to the web - fake secret
-rsconnect::setAccountInfo(name='znpadgett',
-			  token='DA192A4A3FA4FB169FE8B04D20CA9CEA',
-			  secret='XXXXXXXXXXXXXXXXXXXXXXXXXX')
-```
-
 Finally, we examined the relationships between the polling data and the Twitter and Google Trends data post-debate, as well as the relationships between pre- and post-debate changes across data sources.

### 2019-12-11 Presentation/surv727app/app.R

@@ -1,47 +1,54 @@
-#
-# This is a Shiny web application. You can run the application by clicking
-# the 'Run App' button above.
-#
-# Find out more about building applications with Shiny here:
-#
-#    http://shiny.rstudio.com/
-#
+
 
 library(shiny)
+library(rsconnect)
+library(dplyr)
+library(ggplot2)
+library(repmis)
 
-# Define UI for application that draws a histogram
+
+source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/app_data.RData?raw=true")
+
+
+# Define UI
+
 ui <- fluidPage(
-
+    
     # Application title
-    titlePanel("Old Faithful Geyser Data"),
-
-    # Sidebar with a slider input for number of bins 
+    titlePanel("2020 Democratic Primary Candidate Data"),
+    
+    # Sidebar with a dropdown
     sidebarLayout(
         sidebarPanel(
-            sliderInput("bins",
-                        "Number of bins:",
-                        min = 1,
-                        max = 50,
-                        value = 30)
+            selectInput(inputId = "Candidate",                   
+                        label = "Candidate",                  
+                        choices = c("Joe Biden", "Pete Buttigieg", "Kamala Harris", 
+                                    "Bernie Sanders", "Elizabeth Warren"),                   
+                        selected = "Joe Biden"),
+            selectInput(inputId = "Data",
+                        label = "Data Type",
+                        choices = c("Polling", "GTrends", "Twitter"),
+                        selected = "Polling")
         ),
-
-        # Show a plot of the generated distribution
+        
+        # Show plot
         mainPanel(
-           plotOutput("distPlot")
+            plotOutput(outputId = "graph")      
         )
     )
 )
 
-# Define server logic required to draw a histogram
+# Define server logic
 server <- function(input, output) {
-
-    output$distPlot <- renderPlot({
-        # generate bins based on input$bins from ui.R
-        x    <- faithful[, 2]
-        bins <- seq(min(x), max(x), length.out = input$bins + 1)
-
-        # draw the histogram with the specified number of bins
-        hist(x, breaks = bins, col = 'darkgray', border = 'white')
+    
+    output$graph <- renderPlot({
+        all_data %>%
+            filter(Candidate == input$Candidate, Data == input$Data) %>%
+            ggplot() +
+            geom_col(mapping = aes(x=Pre_post, y=Percentage, fill=input$Candidate)) +
+            ylim(0,100) +
[…]

### 2019-12-11 Paper/paper-draft-Padgett-Thiam.Rmd
re-knit paper

@@
 library(pander)
+library(rsconnect)
 ```

### 2019-12-11 Paper/paper-draft-Padgett-Thiam.Rmd
fix formatting and typos

@@
 
+All data used to create the tables, figures, and shiny app in this paper can be found on our Github repository at https://github.com/znpadgett/surv727_padgett_thiam.
+
+### Twitter
+
 Using the rtweet package and the search_tweet function, we were able to gather sufficient tweets for our project and seperated in two datasets; pre- and post- debate.
@@
 We selected severals states such New York, Virginia, New Hampshire, Nevada, Illinois, Iowa, Ohio, California and DC to focus our analysis on.
-
-### Twitter
 
@@
 ```{r, eval=FALSE, include=FALSE}
-post_sent_pos <- data.frame("Candidate" = c("Biden", "Sanders", "Warren", "Harris", "Buttigieg"), 
+post_sent_pos <- data.frame("Candidate" = c("Biden", "Sanders", "Warren", 
+                                            "Harris", "Buttigieg"), 
                        "Positive" =c((sum(sentiments_jb_post$PositivityGI))/27477,
@@
 ## Results
+
+### Data Exploration
+
+#### Twitter
 
@@
 panderOptions('table.caption.prefix', 'Table 1: ')
-pander(table1 ,caption = "Count of tweets that mentionned candidates pre- and post- debate.")
+pander(table1 ,caption = "Count of tweets that mentionned 
+       candidates pre- and post- debate.")
 ```
@@
 panderOptions('table.caption.prefix', 'Table 2: ')
-pander(table2 ,caption = "Count of tweets that mentionned candidates in California pre- and post- debate.")
+pander(table2 ,caption = "Count of tweets that mentionned 
+       candidates in California pre- and post- debate.")
 ```
@@
 panderOptions('table.caption.prefix', 'Table 3: ')
-pander(table3 ,caption = "Sentiment Analysis average positivity score pre- and post- debate by candidate.")
-```
-
-### Data exploration
-
-Because our project was exploratory in nature, we spent significant time exploring each data source.
-
-#### Twitter
-
+pander(table3 ,caption = "Sentiment Analysis average positivity 
+       score pre- and post- debate by candidate.")
+```
+
+##### Create functions
 Create a function to tabulate the count and proportion of tweets by candidates.
 
-##### Create functions
 ```{r, eval=FALSE}
@@
 
+##### Graphing
 A visual of the proportion of tweets pre and post debate
-
-##### Graphing
-###### Pre-debate number of tweets
 
@@
 
-\newpage
 Figure 2 shows the post- debate tweets mentions by candidate.
@@
 ```{r, tidy=TRUE, fig.cap="Pre- and Post-debate Polling Data, by Candidate"}
-polling_data$Pre_post <- factor(polling_data$Pre_post, levels = c("Pre-debate", "Post-debate"))
+polling_data$Pre_post <- factor(polling_data$Pre_post, levels = c("Pre-debate", 
+                                                                  "Post-debate"))
 
@@
 Finally, we examined the relationships between the polling data and the Twitter and Google Trends data post-debate, as well as the relationships between pre- and post-debate changes across data sources.
+We looked at these results for the 5 most popular candidates.
 
@@
   ggplot() +
-  geom_point(mapping = aes(x=Percentage, y=Percentage1, color=Candidate), size=4) +
+  geom_point(mapping = aes(x=Percentage, y=Percentage1, 
+                           color=Candidate), size=4) +
   xlim(0,20) +
@@
 ```
+
+Figure 5 shows that there is no clear relationship between the post-debate twitter sentiment and the polling data. All candidates have similar sentiment scores, regardless of polling percentage.
 
@@
   ggplot() +
-  geom_point(mapping = aes(x=Percentage2, y=Percentage1, color=Candidate), size=4) +
+  geom_point(mapping = aes(x=Percentage2, y=Percentage1, 
+                           color=Candidate), size=4) +
   xlim(0,100) +
@@
 
+In Figure 6, we can see a very slight relationship between the post-debate Google Trends data and polling data, in that candidates polling higher generally had higher Google trends hit rates.
+
 ```{r, tidy=TRUE, fig.cap="Comparison of Changes in Twitter and Polling Data"}
-print(graphing_data)
 pre <-
@@
   select(Pre_post, Candidate, Percentage, Percentage1, Percentage2) %>%
-  group_by(Pre_post, Candidate) %>%
+  group_by(Pre_post, Candidate, Data) %>%
   filter(Pre_post=="Pre-debate") %>%
-  mutate(Pre_twitter=Percentage, Pre_polling=Percentage1, Pre_gtrends=Percentage2)
+  mutate(Pre_twitter=Percentage, Pre_polling=Percentage1, 
+         Pre_gtrends=Percentage2)
 
@@
   select(Pre_post, Candidate, Percentage, Percentage1, Percentage2) %>%
-  group_by(Pre_post, Candidate) %>%
+  group_by(Pre_post, Candidate, Data) %>%
   filter(Pre_post=="Post-debate") %>%
-  mutate(Post_twitter=Percentage, Post_polling=Percentage1, Post_gtrends=Percentage2)
+  mutate(Post_twitter=Percentage, Post_polling=Percentage1, 
+         Post_gtrends=Percentage2)
 
@@
   group_by(Pre_post, Candidate) %>%
-  mutate(change_twitter = ((Post_twitter - Pre_twitter) / Pre_twitter) * 100, 
-         change_polling = ((Post_polling - Pre_polling) / Pre_polling) * 100, 
-         change_gtrends = ((Post_gtrends - Pre_gtrends) / Pre_gtrends) * 100) %>%
+  mutate(change_twitter = ((Post_twitter - Pre_twitter) / 
+                             Pre_twitter) * 100, 
+         change_polling = ((Post_polling - Pre_polling) / 
+                             Pre_polling) * 100, 
+         change_gtrends = ((Post_gtrends - Pre_gtrends) / 
+                             Pre_gtrends) * 100) %>%
   ggplot() +
-  geom_point(mapping = aes(x=change_twitter, y=change_polling, color=Candidate), size=4) +
+  geom_point(mapping = aes(x=change_twitter, y=change_polling, 
+                           color=Candidate), size=4) +
   labs(x="Percent Change in Twitter Sentiment", 
@@
 ```
+
+Figure 7 shows the percent change in Twitter sentiment and percent change in vote share between the two time periods (pre- and post-debate).
+There is no clear relationship between the change in vote share and the change in Twitter sentiment.
 
@@
   group_by(Pre_post, Candidate) %>%
-  mutate(change_twitter = ((Post_twitter - Pre_twitter) / Pre_twitter) * 100, 
-         change_polling = ((Post_polling - Pre_polling) / Pre_polling) * 100, 
-         change_gtrends = ((Post_gtrends - Pre_gtrends) / Pre_gtrends) * 100) %>%
+  mutate(change_twitter = ((Post_twitter - Pre_twitter) / 
+                             Pre_twitter) * 100, 
+         change_polling = ((Post_polling - Pre_polling) / 
+                             Pre_polling) * 100, 
+         change_gtrends = ((Post_gtrends - Pre_gtrends) / 
+                             Pre_gtrends) * 100) %>%
   ggplot() +
-  geom_point(mapping = aes(x=change_gtrends, y=change_polling, color=Candidate), size=4) +
+  geom_point(mapping = aes(x=change_gtrends, y=change_polling, 
+                           color=Candidate), size=4) +
   labs(x="Percent Change in Google Trends Data", 
@@
 ```
-When looking at the pre- and post-debate data from each source side-by-side, we can see that, while candidates who are polling higher have higher numbers of tweets and Google searches (for the most part), there is no clear relationship between the post-debate changes in polling numbers and the post-debate changes in Twitter and Google Trends data.
+
+Figure 8 shows the percent change in Google Trends hit rate and percent change in vote share between the two time periods.
+Again, there is no clear relationship between the change in the two data sources.
+
+In conclusion, when looking at the pre- and post-debate data from each source side-by-side, we can see that, while candidates who are polling higher have higher numbers of tweets and Google searches (for the most part), there is no clear relationship between the post-debate changes in polling numbers and the post-debate changes in Twitter and Google Trends data.
 Regardless of polling numbers, all candidates had higher Twitter positivity ratings and higher numbers of Google searches post-debate than pre-debate.

### 2019-12-12 Paper/paper-draft-Padgett-Thiam.Rmd
Update paper-draft-Padgett-Thiam.Rmd

@@
 
-Using the rtweet package and the search_tweet function, we were able to gather sufficient tweets for our project and seperated in two datasets; pre- and post- debate.
+Using the rtweet package [@rtweet] and the search_tweet function, we were able to gather sufficient tweets for our project and seperated in two datasets; pre- and post- debate.
 The initial dataset contains a little over 1.3 million tweets which was rich enough to proceed with analysis.
@@
 As expected, there was a lot more tweets after the debate than before.
-We used the  Twitter location field to perform analysis at the state level.However, the location column is an open text and not regulated.
+We used the  Twitter location field to perform analysis at the state level.
+However, the location column is an open text and not regulated.
 We selected severals states such New York, Virginia, New Hampshire, Nevada, Illinois, Iowa, Ohio, California and DC to focus our analysis on.
@@
 
-Even with specified keywords, irrelevants tweets were also made it to the initial dataset mainly with the Ukraine issue at the time of pulling.
+Even with specified keywords, irrelevants tweets made it to the initial dataset mainly with the Ukraine issue at the time of pulling.
 We removed all tweets that had the word "Ukraine" in order to focus completly on tweets regarding the debate.
@@
 Next, we seperate the tweets by candidates in order to do analysis at the candidate level.
-It's important to note that one tweets can be addressed to multiple candidates.
+It's important to note that one tweet can be addressed to multiple candidates.
 In that case, the tweet will be found in the each of those candidates dataset.
@@
 tweets <- tweets %>%
-  mutate( date= as.POSIXct(created_at, tryFormats = c("%Y-%m-%d %H:%M:%OS")))
+  mutate( date= as.POSIXct(created_at, 
+  tryFormats = c("%Y-%m-%d %H:%M:%OS")))
 
 df1 <- df1 %>%
-    mutate( date= as.POSIXct(created_at, tryFormats = c("%Y-%m-%d %H:%M:%OS")))
+    mutate( date= as.POSIXct(created_at, 
+    tryFormats = c("%Y-%m-%d %H:%M:%OS")))
 
 df2 <- df2 %>%
-    mutate( date= as.POSIXct(created_at, tryFormats = c("%Y-%m-%d %H:%M:%OS")))
+    mutate( date= as.POSIXct(created_at, 
+    tryFormats = c("%Y-%m-%d %H:%M:%OS")))
 
@@
 #### Sentiment Analysis
-Sentiment analysis of the tweets will not be performed for all candidates but only 5 : Harris, Sanders, Biden, Warren & Buttigieg.
-
-First we need to prep the tweets by removing all non-words such as emojis and use the sentiment analysis package for analysis.
+Sentiment analysis of the tweets will not be performed for all candidates but five selected candidates; Harris, Sanders, Biden, Warren & Buttigieg.
+
+First, we need to arrange the tweets by removing all non-words such as emojis and use the sentiment analysis package [@sentiment] for analysis.
 Althought the sentiment analysis package uses 5 dictionnairies, we will only look at the results from the GI dictionnary.
@@
 
-interest_over_time_all <- rbind(interest_over_time_pre, interest_over_time_post)
+interest_over_time_all <- rbind(interest_over_time_pre, 
+                              interest_over_time_post)
 ```
@@
 freq_tab <- function(x) {
-# make table with count and frequency
 tab <- cbind(Count = table(x, useNA = "ifany"),
@@
 2))
-# get the categories as variable and rearrenge
 tab <- as.data.frame(tab) %>%
@@
 ##### Graphing
-A visual of the proportion of tweets pre and post debate
+A visual of the proportion of tweets pre- and post- debate
 
@@
   ggplot() +
-  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
+  geom_col(mapping = aes(x = reorder(Candidate, -Count), 
+  y=Count, fill = Candidate)) +
     labs(x = "Democratic Party Candidates", 
        y = "Number of Tweets", 
-           caption = "Source: Twitter
-
-                                 Figure 1") +
+           caption = "Source: Twitter") +
 theme(axis.text.x=element_text(angle=90,hjust=1)) 
-
 ```
@@
   ggplot() +
-  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
+  geom_col(mapping = aes(x = reorder(Candidate, -Count),
+  y=Count, fill = Candidate)) +
     labs(x = "Democratic Party Candidates", 
@@
        title = "Post Debate candidates mentions in Tweets", 
-            caption = "Source: Twitter
-
-                                 Figure 2") +
+            caption = "Source: Twitter") +
 theme(axis.text.x=element_text(angle=90,hjust=1)) 
@@
   ggplot() +
-  geom_col(mapping = aes(x = reorder(Candidate, -total), y=total, fill = Location)) +
+  geom_col(mapping = aes(x = reorder(Candidate, -total), 
+  y=total, fill = Location)) +
     labs(x = "Democratic Party Canditates", 
@@
        title = "Pre Debate candidates mentions in Tweets by location", 
-             caption = "Source: Twitter
-
-                                 Figure 3") +
+             caption = "Source: Twitter") +
            theme(axis.text.x=element_text(angle=90,hjust=1))      
-
 ```
@@
        title = "Post Debate candidates mentions in Tweets by location", 
-              caption = "Source: Twitter
-
-                                 Figure 4") +
+              caption = "Source: Twitter") +
 theme(axis.text.x=element_text(angle=90,hjust=1)) 
@@
 ```{r, tidy=TRUE, fig.cap="Pre- and Post-debate Polling Data, by Candidate"}
-polling_data$Pre_post <- factor(polling_data$Pre_post, levels = c("Pre-debate", 
-                                                                  "Post-debate"))
+polling_data$Pre_post <- factor(polling_data$Pre_post, 
+levels = c("Pre-debate", "Post-debate"))
 
@@
   ggplot() +
-    geom_col(mapping = aes(x=reorder(Candidate, -Percentage), y=Percentage, 
-                           fill=Pre_post), color="black",   position="dodge") +
+    geom_col(mapping = aes(x=reorder(Candidate, -Percentage)
+    , y=Percentage, fill=Pre_post), color="black", 
+    position="dodge") +
   xlab("Candidate") + ylab("Percentage") +
@@
                                            "Kamala Harris", "Pete Buttigieg"),                            
-                           "Pre_post" =c("Pre-debate","Pre-debate",
-                                         "Pre-debate","Pre-debate","Pre-debate",                            "Post-debate","Post-debate","Post-debate","Post-debate","Post-debate"),
+                           "Pre_post" =c("Pre-debate","Pre-debate", "Pre-debate",
+                           "Pre-debate","Pre-debate","Post-debate","Post-debate",
+                           "Post-debate","Post-debate","Post-debate"),
                    "Data" = c("Twitter", "Twitter","Twitter","Twitter","Twitter",
@@
       ggplot() +
-      geom_col(mapping = aes(x=Pre_post, y=Percentage, fill=input$Candidate)) +
+      geom_col(mapping = aes(x=Pre_post, y=Percentage, 
+      fill=input$Candidate)) +
       ylim(0,100) +

### 2019-12-12 Paper/paper-draft-Padgett-Thiam.Rmd
knit new version

@@
 
-```{r, message="FALSE", warning=FALSE, results="hide", include=FALSE}
-opts_chunk$set(tidy.opts=list(width=60),tidy=TRUE)
-```
 \newpage
@@
 
-```{r, eval=FALSE, tidy=TRUE}
-
-dem <- search_tweets("#democrats OR #candidates OR #election2020 OR #BIDEN 
-                     OR #sanders OR #warren OR #harris 
+```{r, eval=FALSE}
+
+dem <- search_tweets("#democrats OR #candidates OR #election2020 
+                     OR #BIDEN OR #sanders OR #warren OR #harris 
                      OR #buttigieg OR #steyer OR #yang OR #booker 
@@
 
-```{r, eval=FALSE, tidy=TRUE}
-tweets$BS <-(str_detect(tweets$text, 
-                        regex("#Sanders|@BernieSanders", 
+```{r, eval=FALSE}
+tweets$BS <-(str_detect(tweets$text, regex("#Sanders|@BernieSanders", 
                               ignore_case = TRUE)))
-tweets$KH <-(str_detect(tweets$text, 
-                        regex("#harris |@KamalaHarris",  
+tweets$KH <-(str_detect(tweets$text, regex("#harris |@KamalaHarris",  
                               ignore_case = TRUE)))
-tweets$JB <-(str_detect(tweets$text, 
-                        regex("#biden |@JoeBiden", 
+tweets$JB <-(str_detect(tweets$text, regex("#biden |@JoeBiden", 
                               ignore_case = TRUE)))
-tweets$EW <-(str_detect(tweets$text, 
-                        regex("#warren |@ewarren", 
+tweets$EW <-(str_detect(tweets$text, regex("#warren |@ewarren", 
                               ignore_case = TRUE)))
-tweets$PB <-(str_detect(tweets$text, 
-                        regex("#buttigieg|@PeteButtigieg", 
+tweets$PB <-(str_detect(tweets$text, regex("#buttigieg|@PeteButtigieg", 
                               ignore_case = TRUE)))
-tweets$TS <-(str_detect(tweets$text, 
-                        regex("#steyer | @TomSteyer", 
+tweets$TS <-(str_detect(tweets$text, regex("#steyer | @TomSteyer", 
                               ignore_case = TRUE)))
-tweets$AY <-(str_detect(tweets$text, 
-                        regex("#yang| @AndrewYang", 
+tweets$AY <-(str_detect(tweets$text, regex("#yang| @AndrewYang", 
                               ignore_case = TRUE)))
-tweets$BC <-(str_detect(tweets$text, 
-                        regex("#booker | @BookerCory", 
+tweets$BC <-(str_detect(tweets$text, regex("#booker | @BookerCory", 
                               ignore_case = TRUE)))
-tweets$AK <-(str_detect(tweets$text, 
-                        regex("#klobuchar | @amyklobuchar", 
+tweets$AK <-(str_detect(tweets$text, regex("#klobuchar | @amyklobuchar", 
                               ignore_case = TRUE)))
-tweets$TG <-(str_detect(tweets$text, 
-                        regex("#gabbard |@TulsiGabbard", 
+tweets$TG <-(str_detect(tweets$text, regex("#gabbard |@TulsiGabbard", 
                               ignore_case = TRUE)))
@@
 Note that tweets during the debate (9 - 11 p.m.) were removed.
-```{r, eval=FALSE, tidy=TRUE}
+```{r, eval=FALSE}
 pre_debate <- tweets %>%
@@
 
-```{r, eval=FALSE, tidy=TRUE}
+```{r, eval=FALSE}
 pre_sent_pos <- data.frame("Candidate" = c("Biden", 
@@
 
-```{r, eval=FALSE, tidy=TRUE}
+```{r, eval=FALSE}
 register_google(key = "XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX")
@@
 
-```{r, tidy=TRUE}
+```{r}
 github_link <- "https://github.com/znpadgett/surv727_padgett_thiam/raw/master/Data/Project%20polling%20data.xlsx"
@@
 
-```{r, tidy=TRUE, fig.cap="Pre- and Post-debate Google Trends Data, by Candidate"}
+```{r, fig.cap="Pre- and Post-debate Google Trends Data, by Candidate"}
 interest_over_time_all$Pre_post <- factor(interest_over_time_all$Pre_post, 
@@
 For the polling data, we looked at the pre- and post-debate polling numbers for each candidate.
-```{r, tidy=TRUE, fig.cap="Pre- and Post-debate Polling Data, by Candidate"}
+```{r, fig.cap="Pre- and Post-debate Polling Data, by Candidate"}
 polling_data$Pre_post <- factor(polling_data$Pre_post, 
@@
 
-```{r, tidy=TRUE, warning=FALSE, message=FALSE}
+```{r, warning=FALSE, message=FALSE}
 #clean data
@@
 Then, we created a shiny app, which can be viewed at https://znpadgett.shinyapps.io/surv727app/:
-```{r, eval=FALSE, tidy=TRUE}
+```{r, eval=FALSE}
 # Define UI
@@
 
-```{r, tidy=TRUE, fig.cap="Comparison of Post-debate Twitter and Polling Data"}
+```{r, fig.cap="Comparison of Post-debate Twitter and Polling Data"}
 graphing_data <- cbind(twitter, poll, gtrends)
@@
 
-```{r, tidy=TRUE, fig.cap="Comparison of Post-debate Google Trends and Polling Data"}
+```{r, fig.cap="Comparison of Post-debate Google Trends and Polling Data"}
 graphing_data  %>%
@@
 
-```{r, tidy=TRUE, fig.cap="Comparison of Changes in Twitter and Polling Data"}
+```{r, fig.cap="Comparison of Changes in Twitter and Polling Data"}
 pre <-
@@
 
-```{r, tidy=TRUE, fig.cap="Comparison of Changes in Google Trends and Polling Data"}
+```{r, fig.cap="Comparison of Changes in Google Trends and Polling Data"}
 change_data %>%
